\input{eqns.tex}

\chapter{The Case of the Night-Runner}

The dim moonlight diffused through the ever-waking boughs of cedars rustling in a gentle lullaby among the placid wind.  The nearby creek, once a leviathan waterfall from the distant peaks, flowed as it always did. A young person with flowing lavender hair in open clothing sat on the birch-plank floor of the fifth-story loggia, enjoying a rare hour free of mundane housework. Cytaen Myllada, no more than thirteen years of age at that time, once could fantasize of tales and legends, war and peace, the great and the small, that lay beyond the cedars, or even this village, and had even written of them, but now her imaginations had nearly run out. After all, speculating what is there does not compare to actually knowing what is there, nor does mere knowledge compare to seeing these places firsthand.

Myllada also held a long-standing interest over mathematics and nature, interests that her parents, allegedly desiring an ignoramus to perform chores and marry young, would not tolerate. Having seen no interior of a school or library, she had learned to read using a book she had received eight years ago from an eccentric instructor, stashed in a closet alongside seven score pages of her own writing, avoiding the wrath of the flame.

By then, this inquisitiveness had vexed the young person for no fewer than three thousand nights in the confines of the mansion uneroded by time, wherein one could not find any traces of modern society.

The unexpected clamor of bushes snapped her out of reverie. Myllada, who seldom had the opportunity of conversing with those outside her family, transitioned into a kneeling position, peering over the rails in order to discern who, or what, made that sound.

Flashing a cloak as dark as the rest of its outfit, a form scurried along the side of the building.

Loudly enough for the figure to hear the sound, but quietly enough to avoid waking up anyone else in the house, Myllada whistled.

The figure stopped and turned around, running to the source of the whistle.

Knowing that any speech would attract attention, Myllada brandished her hand, receded into her room, pulled out a sheet of paper and a pen, and scribbled a message before folding the paper several times and tossing it onto the needle-covered grounds, ensuring that the letter did not land on a lower loggia.

The note thudded on hitting the ground, at which the unidentified scampered to collect it, before bowing shallowly and making haste out of the forest.

As the surroundings of the house again became desolate, Myllada again felt the hopelessness of residing there. But with this cloud came a silver lining: the narrowest probability that whomever she spotted would respond to her plea; help her escape the wretched prison.

\centeredstars

As the sun rose, a person, having returned home not long ago, opened a note that flew from a mansion untouched by centuries past. Not only was the letter unsigned, but the handwriting flew in all directions, hardly organized, and a style unexpected from someone who would live in such a place.

\q{
	I have been stuck in this house for many years, without a day of school, being raised as an ignoramus whose only purpose is to maintain the house and marry young. You are one of the few people other than family members whom I can reach.
	
	Please consider replying by any feasible measures. If I find you helpful, then I will find something for you in return. Make sure to arrive at night and bring clothing.
}

The recipient wondered why the sender asked for clothing -- perhaps the sender was naked? In any case, there was work to be done, to which the message was completely irrelevant.

\centeredstars

By midday the excitement over the mysterious visitor has eroded, and the possibility of any further external contact seemed a distant dream. \emph{That person will never come; what do I have in return?} Myllada pondered as she swept the corridors, lapsing for a few seconds.

``A woman who does not sweep is worthless!'' came a deep yell behind her, shocking her back into the monotonous task.

\emph{I could count the people who use that word with one hand. Well, on the bright side, if I'm worthless, then it shouldn't matter much to get out of here!} Myllada humorously concluded while joining thought and movement into the same rhythm. \emph{But, of course, I can't just brazenly say ``I'm useless to you'' and frolic out through the door.}

\centeredstars

Once again the moonlight diffused through the tree-branches and save the ever-running creek and the whispering of the trees all was quiet. Myllada was in her room tonight, lying in bed, when she heard the familiar clamor of bushes and opened the door to the loggia in response.

It appeared to be the same night-walker, now peering upwards toward her vicinity. The figure observed the trees, as if it were finding a path into the house, but after a long moment, it left behind a large sack and ran away into the depths of the woods.

\emph{Whatever it left... it must be coming back, but for what?} pondered Myllada as she receded to her room. She opened the closet door and pulled out a stack of papers hidden behind the immodest clothing she had. Kneeling toward the moonlight, she picked up random pages to read and held them to the air.

\q{
	Sturdy wooden bridges span the mountains between which the river was born, connecting the buildings suspended in the air. Most of the rooms are open to the cold air, with tall windows with no glass.
	
	Near the valleys tunnels a \emph{veten} wide are bored in the walls of the mountains, leading to mineshafts reaching up to three \emph{navso} underground.
}

And another:

\q{
	In the forests to the south there once existed a great city, two \emph{navso} across, whose tallest structures could be observed from eighty \emph{navso} away. One who traveled through it would be confused about whether it was day or night.
	
	It has been long since it was flattened to ruins, but several visitors still frequent a mysterious shack near its center --
}

Hearing a whistle, Myllada opened the door to the loggia and noticed a contraption brought by the night-runner -- what seemed to be a tray with a crank to the side.

Upon depositing the sack onto the tray, the figure turned the crank, causing the machine to lift the tray up to the fifth floor using some sort of metallic arm.

Myllada retrieved and opened the sack, finding a pair of sandals and a plum-colored robe. Inside the robe was the note she had sent, with a message on the back: \emph{Can you get out?} to which she, still in the open dress, and discerning that the platform obviously could not support a human being, took out a pen and replied:

\q{
	All of the doors are sealed. Perhaps I could jump off, but how would I return?
}

\chapter{The Tailless Long-Tail}

When Myllada rose again in the morning, she felt that she had not slept enough, but her father was yelling for her in the voice she had learned to abhor. Her name, her appearance, her voice -- she detested nearly everything in her current life, but now was the wrong time for absentminded mentation, and she reluctantly stood up and opened the door to the rest of the edifice.

At the table over the early meals, always eaten in sleeping-clothes, her father inquired, ``Thou lookest half-asleep. Hast thou been awake all night?''

``I have not,'' replied Myllada, while sipping her tea. The taste, she noticed, was slightly exotic.

\centeredstars

Another night fell and Myllada was alone in her room, putting on the clothing that she received the past night and anticipating another visit, reading her old compositions to keep herself occupied.

Suddenly, she felt exhausted and could not concentrate on the passages. A desire to sleep encroached on her mind, more influential than the anticipation of a friend, and she, still covered to the feet and down the arms, unfolded her body and laid her head on her right arm, allowing a curtain of darkness to descend.

\centeredstars

Myllada woke up, face in a bucket of water. To the side there was a person no more than four and twenty years old, with short dark brown hair, as well as a lantern, which was somehow lit without a flame.

Rising into a sitting position, Myllada asked, ``How did you get in?''

``One of the windows wasn't sealed properly. My name is Darmjarel Telto.''

``Cytaen Myllada. Where's your tail? I can't find it.''

``I'd like to look at your necklace. It looks quite attractive on you.''

Myllada pulled out a fine golden chain fitted snugly around her neck. The red gem at the front was cut into a rhombus, but there was an orange mist trapped inside it.

Telto almost jumped in surprise. ``This is a \emph{tracking charm}. Long since they've been banned. As long as it's on, whoever put it there knows where you are. Severing the chain isn't of any use either; that person will be notified with immense pain. Now if you could find where the two ends of the chain were connected, you could disconnect them and avoid these measures. However, the necklace is hot to the touch for anyone but the wearer.''

``Now, how difficult is disconnecting the two ends like that?''

``Finding the joining point isn't too difficult; you can just look for an abnormality in the chain. The hard part is actually disconnecting them without triggering the notification; as doing so requires precision. Even connecting the charm into a full circle is a huge feat.''

``That's almost impossible, much less doing it the night of your escape.''

``If they dare to use forbidden magic like that,'' pointed out the acquaintance, ``they wouldn't hesitate to kill a person of anything less than pure blood. This is a dangerous place to meet; we should gather a short distance from here. A sleeping person can't track you, of course. And for this purpose, I brought something.'' Telto pulled a knotted rope out of a sack. ``Tie this to one of the pillars out there and climb down. And take a bag too.''

``Thank you very much.''

``So you can read and write, is that correct? Do you enjoy it?''

``I can. I used to enjoy writing, but now my imagination has run out. At the same time, I'd like more books to read.''

``I'd like to talk more, but morning is approaching, and I'd like to survive. I will see you next night.''

While Telto, carrying the lantern, leaped from the loggia, Myllada started stashing the rope and the bag into the closet and changing into the open dress, crawling into the bed before sleep caught her again.

\chapter{The Spire to the Sky}

The old man Nasrelten opened the door to his daughter's room. ``Why is there a bucket of water in thy room?'' he pointed to a wooden bucket half-full of water, with a puddle surrounding it.

To which Myllada, warm blood circulating through her appendages, replied, ``The room was hot.''

``Beware: I am not a foolish man. If thou thinkest of departing without my consent, I will promptly encounter and escort thee back here. Now let us eat.'' The old man left toward the table.

Myllada had no choice but to follow the old man, and she recalled the tea tasting slightly unusual. \emph{Perhaps it contained a sleeping ingredient.}

\centeredstars

Once again did night fall, but so did a heavy rain, sliding off the leaves and assimilating into the ground. Myllada, not wanting to read that night, knelt toward the exterior in the clothing given by Long-Tail, with the rope to her side.

The pattering of the rain muffled the whistle, but Myllada could detect it; in response, she opened the door and walked outside to tie the rope to one of the pillars and slide across it onto the muddy ground, making a splash and dirtying her feet. Without saying a word, Telto ran away, prompting Myllada to follow her under an old spruce tree, whose soft floor of spent needles were moistened only by the occasional drop of rain that managed to pass through the canopy.

The cold light from the lantern turned on, lighting the underside of the tree with a white glow. Telto opened her own bag and took out a small book.

Looking at the pages, Myllada scooted herself beside Telto while she opened the book and started reading aloud, following the elegantly printed letters.

\q{
	In the great days of Asnar, winter came every year and covered forests and plains in an untouched blanket of snow. Winter after winter, the snowflakes flew down onto the ground and piled up two \reasyr high, and the two sisters frolicked across the land, leaving no footprints, neither above the other.
	
	That is, until the fall of Asnar and the succession of Fenran, when the snow clouds advanced less and piled up lower each year, and the summers grew warmer. They prayed to the Commander of the Sky to undo this effect, yet still the snow melted more quickly every spring and became less inclined to visit when autumn had stripped the trees of their leaves.
	
	At last on the end of winter of the 1289th year, when the snow piled up no more than a half \emph{reaser}, the elder one cursed the Commander for the diminishing cold season.
	
	In hearing this curse, the Commander snatched the gift of coldness and imposed an eternal summer where they dwelt, to the degree that even the shade became too hot for the two. The sun scorched the mud into bricks, and the river fell an \emph{avanta}.
	
	The younger sister, while seeking retreat in the lukewarm stream, thought and told to the elder about building a spire to reach the heavens and knock down its potentate.
	
	For sixteen years they advanced the heavens, brick by brick, digging the ground for materials, forming the walls and the stairs, no longer being equals but rather having the elder command the younger.
	
	After sixteen years of sweltering heat, the spire reached half of the clouds, overlooking the Evil-Telling Mountain, and with a bow they shot the Commander from her cloud, dropping her onto hard soil. The spire toppled, dropping the sisters onto the earth, their falls softened by the white layer deeper than ever before.
}

Myllada interrupted, ``They didn't start speaking a different language than before, did they?''

Telto paused for a few seconds for a breath, the replied, ``They still spoke the same language: our language.'' She continued:

\q{
	Upon seeing the spire topple and the ground shake, magicians from the surrounding areas investigated what happened. They found the remains a suitable place for them, as their insides felt warm and filled with magical power.
	
	The newcomers showered thanks onto the sisters for a shelter. They replaced the mud-brick walls with stone and lit the interior with torches, and near the edges, they built new rooms.
	
	What was the center of the spire became a great library, lit by the sky, with more than one million books, the shelves towering like the trees of an old forest, filled with works from all directions and distances, from the common to the esoteric.
	
	Across a door, the air was warmed by giant candles, and the walls were made of sandstone from the deserts. Scrolls and books spanned the tables, their text in an illegible script.
	
	And across the hallway, beyond another door, once an underground river was a great canal, two and a half \emph{navso} long. If one manages to swim that distance, then one encounters another door.
	
	Past that one is a garden of unusual, almost otherworldly flowers. It seemingly floats in outer space, the stars shining brightly, and yet another door lies at the end.
	
	What is beyond \emph{that} door? A former resident has been known to construct esoteric devices, but has long since left for greater ambitions. No one knows if there is another door, let alone what may exist behind it.
	
	And thus the edifice came to be known as the Castle of Magic Snow.
}

Myllada added, ``I apologize for being asleep last night.''

``An ingredient with an unpronounceable name. Ingest it in the morning; be quick asleep at night. Where did you find it?''

``I suppose it was in my morning tea. If I don't drink it, though, the old man will get suspicious.''

``Could you swap the glasses when he's not looking? I could make a distraction.''

``Only when no one else is looking.''

For a short time, only the rain made any sound, while the halo of scarlet light made its first appearances in the east. Telto lifted Myllada, carrying her to the rope back up.

``Let me have your clothes and I'll bring them clean next night.''

Feeling guilty for having another person do her chores, but at the same time knowing that doing so was also the only way not to get caught harboring a friendship forbidden by her parents, Myllada climbed the rope and took off her clothing. She threw them down and, after untying and stowing the rope, collapsed on the bed naked.

\chapter{The Law of the Tetradeus}

The next morning, the rain ceased to fall, and Myllada, more pallid than usual, could hardly wake up that, when the old man came into her room, he thought that she might be ill.

``Art thou well, my daughter?''

Recognizing the opportunity for a day off, Myllada, remaining in her bed, replied, ``No, I am not.'' Now that she gave that answer, she truly might not have felt well.

``Then thou shalt remain in bed. Be dressed, but do not overwork thyself.''

\centeredstars

While Myllada was in need of more sleep, the day was still dull and uneventful when she was awake, and, without a clock in the room, she scrutinized the passing of the clouds across the vivid blue sky through the window, imagining kingdoms behind them. However, she knew from the book that clouds were formed from water vapor, throwing her imagination through the clouds, into the ground.

And that the sun was a star (contrary to what the old man insisted), too hot to live on.

Or that the stars were too far away to visit.

Or the moon only reflected the sun's light.

Or trees can only become so tall.

Or the world did not expand in a plane into infinity, but rather into itself as a sphere.

Or the Castle of Magic Snow was only a tale, and not reality.

Even if it were, would the sisters have been more content if the snow did not recede and the castle had never been built, or if all happened as in the story?

And \emph{this} reality was only several \emph{etago} in area, devoid of knowledge, with no worthwhile endeavors, only the drudgery of housework, or when fortunate enough to be ill, lying in bed, and doomed to commit early to another person whom she could not choose -- except that this reality was not the only one, and today she could jump out of the window and abandon it forever -- if only she had not dirtied her clothes yesterday night.

Myllada stretched her arms and extended the right one over the lower area, rubbing it like the gentle breeze blowing through the window (which the old man had left open), until the knob turned and the back door creaked --

``\emph{Myllada!}'' gasped and scolded the old lady Cytaen, who arrived to take her to a bath, quickly cocking her head away and covering her eyes. ``Why is thy hand where it is?''

Unable to speak, Myllada slowly shifted her hand away from the area. ``No, no reason! It was just a coincidence, mother!''

``Now come with me.''

More energetic than at sunrise, Myllada, still in bed-dress, followed her mother down the stairs, toward the bathing room, a granite chamber with the only windows being the wide ones near the ceiling, entering one of the doors inside while the old woman retrieved several buckets of water.

Now without any clothes, Myllada felt a rough, soapy cloth scratch her, with torrents of water continually raining down, before the woman, strapped \emph{nenfya} drenched, rubbed her body with soft towels and wrapped a long, thin sheet around her many times and pushed her into the water.

Even the sheet did not dull the pain from the ice-cold water -- not to mention the bucketfuls that her mother poured over her head every ten seconds, leaving Myllada unable to admire the scenery through the windows. Beneath her audible shivers was a silent prayer to not die from hypothermia -- to see it stop any time. Just as the frigidness was about to surpass Myllada's endurance and she was about to start screaming and pass out, her mother commanded sternly, ``Get out.''

The young person processed a thousand different apologies and promises through her head before she felt the sheet being unwrapped from her and towels drying her, this time, more thoroughly, giving a hint that the brutal coldness was now over.

Her mother, gently enunciating, ``Thou seem'st well enough,'' dried herself and carried her child on her back to another door. On letting Myllada slide off her back, the old woman covered her with a delicate layer of chalk from head to toe.

\emph{Great, well enough for some festival. I'll probably walk limp for the rest of my life too.}

\centeredstars

They arrived by apparition to a garden near a brick houses, Masters Nasrelten and Cytaen wearing masks, with the elder child of the latter name beside them. (The younger child, naturally, was still at home, too young to attend.) Candles gave a dim but sufficient light on the many-colored flowers, while quiet music played in the background.

Having been exacted to stay at her parents' side and not wishing for retribution, Myllada clutched her mother's hand, whispering, ``I do not feel that well.''

``Please stop making excuses.''

``I really don't --''

Myllada felt a pinch on her back.

\centeredstars

Two hours passed, with Myllada passing them by fondling the grass and the flowers, when she heard her name. She looked up, wondering why she was needed, when her parents pointed to an evacuated center, occupied only by another man, as well as a boy two years older than she.

Myllada took several steps in that direction, but suddenly she gained an insight on what was happening and took a step back.

The crowd went quiet.

``Go forward.''

Several seconds passed before Myllada scurried, still barefoot, although even doing so quietly didn't prevent the others from noticing her run away.

Myllada jumped around the mansion a quarter of the way before she hopped into a bush to buy a few more hours.

\centeredstars

Four hours passed when Myllada felt a touch and suddenly found herself at home. The mother sobbed, her tears washing away the powder off her face.

The old man Nasrelten first uttered a single word: ``What?''

Myllada felt that if she waited a few minutes --

``What is thy problem?'' the old man exploded in fury.

Not knowing how to reply, Myllada froze in dread --

``\emph{What is thy problem?}'' repeated the enraged person.

``That...'' and she paused. ``I am worthless to you and therefore should be forced out of this family.''

In a softer voice, the old man refuted,

\s{
	What will thou get outside this home, thou wretch, \\
	For what a cold and bitter place that is \\
	And weak in mind and body thou canst be --
}

``Because you made me so, and when you die!'' raised she the volume of her silky voice.

The response appeared in a firm tone, ``By the time we perish, thou wilt be married.''

``I do not wish to be married -- to depend on another mortal for my success.''

``This is against the nature created by the Four Gods; when it is shattered, the shards will stab society.''

``And when you prove that there are four gods and no more; when you prove that they wrote rules; when you find the correct one, then I'll gladly marry.''

As a reaction the old man collapsed, and his spouse, wiping up her tears, warned, ``It has already been too late to return. Carry thy father to the room, and beware that I expect the entire house cleaned by sunrise,'' before returning to wash herself and go to bed.

Myllada, on the other hand, walked down the stairs to the basement, gathering a broom and a rag, and back up to the first floor to carry her father to the room. She wet the rag and picked up the particles of chalk remaining on the floor, then returned to the basement and sat on the floor until she was sure that both of her parents were sleeping.

After half an hour, she checked to see that the bathing-room was unlit, and washed herself there in the dark (after all, it is hard to clean a house when covered in chalk).

Managing to discern some footsteps on the southern side of the domicile, Myllada crawled up the stairs to her room. The familiar sound of the flying tray started, and she picked up the clean sandals and robe, as well as a wide-brimmed hat, all of which she put on in her room before taking the blanket and running to the kitchen.

It did not take long for her to reappear with a sack full of food. Myllada pulled out two sheets of paper; on the first, she wrote, in the most haphazard handwriting that remained legible:

\q{
	I AM WORTHLESS TO YOU!
	
	MAYBE I WILL BE MORE USEFUL TO SOMEONE ELSE!!!
	
	SIGNED, YOUR USELESS FIRSTBORN!!!
	
	(P.~S.~I took some of your food; it should be less than what you spend on me.)
}

On the second, more neatly:

\q{
	Just escaped the union.
	
	We're going for good. Gather a pile of leaves below.
	
	Bringing some food too.
}

Myllada left the first note on her bed (not hers anymore) and the second on the flying tray. Telto wound the crank the other way, eagerly read the letter, and piled up leaves a half \emph{avanta} high.

Meanwhile, Myllada packed the book and her loose writings into her bag, coiled the rope over her left shoulder, and jumped off the ledge...

\chapter{A Divine Promise}

Myllada landed with a soft thud, albeit with her hair all over the place and her hat off-center.

Swiftly and lightly did Telto run, hardly making any sound, and swiftly and lightly did Myllada follow her. By then the moon was only half its size, but the stars shone almost as brightly as it did on the first encounter.

Behind bushes and trees, Telto had cut eight of the iron bars from the fence, and near that opening Myllada stopped. ``Give me the knife.''

Telto handed Myllada a makeshift knife, with its blade sticking out at a peculiar angle from the handle, now wrapped in paper. Myllada first made two cuts through her hair at the shoulder level, and then took out the amulet, aimed for the chain, and pulled the blade through it, grinning as she heard a distant cry of pain.

Dropping the severed necklace, the two dashed through the improvised exit, straight toward an unpaved dirt path...

\centeredstars

While Telto was experienced with running long distances, Myllada was wound down when they reached a small wooden hut next to a lake. It had few windows, all of them plain, and a boat was propped to its side.

Telto opened the door and turned on the lantern. Myllada followed, silently appreciating the austerity of the interior.

``I live with my parents here. Let's scare them,'' whispered Telto.

As they crept toward the bed, Telto put down the lantern.

\centeredstars

``What in the world are you doing this late?'' gasped the one with Telto's hair.

The other, with long red hair, added, ``You almost scared us to hell!''

``I came here with someone,'' Telto pointed to Myllada.

The dark-brown-haired one asked, ``Do you two know each other?''

Myllada answered, ``Yes.''

And the red-haired one: ``Anyway, we always welcome visitors.''

The red-haired person, appearing forty-eight years old, flipped a lever, flooding the kitchen with a cold white light.

Curious of what arcane sorcery could generate light without a fire, Myllada questioned, ``How did you light the room like that?''

``Electricity,'' that person chuckled. ``Did you travel through time?''

``Her parents wanted her to marry young, so I'd say so figuratively.'' Telto, too, wanted to know more about Myllada's origins.

``What's your name, young person?''

``Cytaen Myllada. It seems to me, too, that I've stumbled into the far future.''

``Ercelco \sypros,'' introduced the red-haired person, who promptly drew five fish out of a white box and carefully placed them on a pan.

``And my name is Darmjarel Cidene,'' followed the brown-haired one. ``Telto, even you look weary. How far did you run?''

``Six \emph{navso} forward and six back. For my partner it's just the six back.''

Noticing that Myllada was taking a loaf of bread from her makeshift sack, Cidene thanked her. ``What brought you here, stranger?''

``I didn't like living there. Couldn't go to school at all --''

``(\emph{Nalarylar marahatan es,} what kind of parents were hers?)''

``and had to teach myself how to read, forced to wear immodest --''

``(\emph{speak of the devil!})''

``and, in general, held worthless unless I was cleaning the house or something. I first saw Telto four days ago, in fact. Dropped a note, and surprisingly she came back the next night. The night after, I fell asleep. This person found an open window, climbed inside, and submerged my head in water.

``She asked for my necklace, which was actually a tracking charm. It's fortunate she noticed; otherwise, we'd be doomed by morning! I told her that I wanted to read more books,

``and the following night in the heavy rain, she brought a book and read it with me under a tree --''

``(that explains the dirty clothes! If I'd known --)''

``I returned the clothes to her for the day, so content that I forgot to put on clothes before going to bed.

``I was sleepy the next morning, so my father thought I was sick, so he left me in bed. Spent most of my waking hours staring at the sky --'' she carefully omitted the part about onanism -- ``until my mother opened the door to take my bath. That was cold enough for me to think I'd be walking limp for the rest of my life.

``Then she spread chalk on my body, and I wondered what was happening. Took me down to the closet so I could put on an outfit -- of course, showing the sides (speak of the devil again) -- and my parents and I held hands.

``We suddenly appeared at a garden near a brick house, filled with soft chatter and thousands of candle-flames, reminding me of fireflies. At the center was a stone-brick circle, with six paved paths diverging, their borders delimited by trellises.

``For the most part, I was bored. There was food, but I had to be careful enough not to wipe off the chalk. I spent most of my time with the grass and flowers.

``Then my parents called me and pointed at the circle, where a priest stood with an open scroll and a young person a few years older than I was. I eagerly took the first three steps before realizing what they were trying to do.

``Knowing that I couldn't go forth, I ran back instead, across one wall of the mansion, and jumped into a group of shrubs and hid in a hole.

``By the time I was found, it was too late. I saw myself back at home, one parent crying and the other raging in disgruntlement. I don't remember the whole discussion, but I do recall that not marrying was against the law of the gods.''

``How many gods?'' interrupted Telto.

``Four. I've probably angered them quite a lot.''

\sypros, still frying the fish, chimed in, ``Ah, but we believe in only one god, who loves all who act kindly and use reason.''

``Just imagine what would have happened if all hadn't occurred as planned,'' added Cidene. ``I know what I'd do if I were the old man in that case. I'd let you back in, give you a warm bath, and find the real reason that you'd want to be somewhere else.''

Myllada rested her arm on the table, lowered her head, and let her tears be absorbed. ``I'm sorry... you are the kindest people I've ever met.''

``Well, you've known only three other people, right?'' answered Telto. ``It's a fifty-fifty chance.''

By then, the cooked fish arrived at the table.

Myllada continued, ``eventually, he decided to make me clean the whole house that night --''

``(that's unreasonable.)''

``and sometime later, when the rest of the family was sleeping, I listened to Telto's footsteps and the sound of the flying tray. Got back the clothes she gave to me, took some of the food, and wrote them a note.''

``\emph{What did it say? What did it say?}''

``Ah, I definitely memorized that.'' Myllada took a deep breath --

\q{
	I AM WORTHLESS TO YOU!
	
	MAYBE I WILL BE MORE USEFUL TO SOMEONE ELSE!!!
	
	SIGNED, YOUR USELESS FIRSTBORN!!!
	
	(P.~S.~I took some of your food; it should be less than what you spend on me.)
}

Explosive laughter.

``Asked my friend to pile up some leaves for a soft landing, and jumped over the rails. When we reached the place where some of the iron bars were severed, I asked Telto for a knife. Cut my hair -- it used to reach over here --'' pointing somewhere mid-back -- ``, you know -- and that tracking charm, and buried both of them in the ground.''

\centeredstars

The sun was now rising.

Myllada helped herself up. ``Well, I have to go soon. I don't want to land on square one again.''

``Telto,'' Cidene asked, ``you're going with your friend, right?''

``I will.''

``I pray for both of you; make it back alive!''

The birds sang the song of the morning sun, and the lake reflected the axiomatic scarlet glimmer. Myllada and Telto continued along the path, satiated from the late dinner and feeling reinvigorated.

From then on Myllada found it more fitting to believe in their god and to follow their advice.

\chapter{The Island Feared Even by Dragons}

The dirt path gradually vanished and became only a line clear of trees, and when there was no actual grassless area anymore, the trees, displaying the newborn leaves, closed down until the clearing was only two \emph{avantar} wide, too narrow for two people to travel abreast, and thorny brambles spanned the path. Myllada, her hat now tied to her back, was grasping Telto's shoulder in order to avoid falling.

Telto couldn't handle another person's weight. ``Stop grabbing my shoulder! I might fall too!''

Myllada complied and knelt on the ground, digging through yesterautumn's deciduous leaves, and fished out a straight stick that towered to her shoulders, firmly prodding the ground with it. ``Sorry, didn't want to lose my balance.''

\centeredstars

In an half hour the forest opened to a wide, rushing river foaming white, unsuitable for swimming. Not far from them was a shelter constructed from a cliff, and fishing nets scattered in its vicinity.

Myllada put on her hat as they approached the house, leaving prints in the sand.

Out of nowhere, a stray arrow flew across the air as Myllada felt a heavy tug on her robe. Only then did she read the sign:

\m{
	There is NOTHING free here!
	
	Trespassers WILL be shot!
}

``Stop being careless here; this isn't your home or mine anymore!'' warned Telto as she tore down the post and scurried back into the every-man's-land.

Another arrow flew and hit Telto's back --

\centeredstars

They were now inside a small cave in the middle of the forest, lit only by the electric lantern and the stars, the unreachable stars.

``Why'd you tear down the sign post? That was probably an absurd act.''

Telto remained silent as Myllada cleaned her wounds and laid down the stick that was retrieved to her side.

\emph{Surely she must have a reason, however unusual. I wouldn't shoot everyone coming on my land, but if someone broke... In any case, we're completely defenseless here.} ``Can you stay here for some time?''

``What reason?'' Feeling a fraction of the pain she did before (as well as mild humiliation), Telto put her clothing back on.

``Gathering materials.''

``I'd say proceed.''

Myllada did gather sticks and cut thorns, but, in fear of losing her friend, never lost sight of her.

\centeredstars

Another day, of course, came, and Telto arose.

Amused by the amount of sticks, vines, and food retrieved (Myllada consulted her book for every plant collected), she smiled and immediately took some of the sticks and vines.

Not having slept for a day and a half, Myllada laid her head on Telto's lap, watching her friend weave a net out of those vines.

\centeredstars

The sun's feet touched the horizon, splashing a splosh of pink and orange. Myllada found herself lying down on grass, next to the river, where Telto, holding a handle to a net, was catching fish. Myllada tidied her hair and started to sit to the left of Telto.

Noticing someone on her side, Telto commented, ``You don't seem afraid of many things. I can run farther than you, and I can catch more fish in a day, but I still fear the unexpected arrows and imaginary creatures in the dark.''

``As long as you're here, the only fear I have is of my family.''

Telto picked up two of the baskets full of fish. ``Well... I'm exhausted. I'm going back to the cave.''

And Myllada followed, two more in her hands and bag over her shoulder.

Without prior notice, the ground shook lightly and the river gave a heavy splash. A malachite-green serpent, its rhombic scales as long as a human hand, coiled itself above the surface.

In response to the event, Myllada and Telto turned around.

The dragon lunged toward the land, and Telto bolted farther inland, Myllada tailing her, into the cave. Still spotting the creature heading at the shelter, the former retrieved one of the sticks and a vine. In rage, she held the vine like a whip and released it --

Crying in pain with bloody hands, Myllada caught the thorn. ``Stop! That won't hurt it!'' A fish flew into the air, and the dragon flew toward it, returning when it caught the bait.

But the dragon returned not to attack. It arrived more slowly, crawling and waiting for something.

By the time Myllada climbed up its body, caressing its head, Telto realized what the former had done. ``That is the \emph{Eltesa Ardan}, the river dragon... how did you befriend it? I haven't heard of a single person do that.''

\centeredstars

As the \emph{Eltesa Ardan}, carrying two passengers and their luggage, neared the center of the river, it headed for an island located there and slowed down.

Myllada and Telto jumped onto that island, one where the sunlight never touched the ground and the water glowed purple.

``What happened there?''

``Somehow afraid to continue rest of the way.''

``That doesn't make sense, unless that involves getting lost. In any case, we're stuck here, and we need a way to reach the other side.''

This time, the younger one led the way, her hands still dripping. As the drops of blood hit the river of purple, they vanished, producing a harsh fizz.

Higher up the mound, thirty \emph{avanto} above the shore, the trees thinned out, and the ground became black ash. Storm clouds, waiting to shower luminescent rain, hovered from where the trees stopped. The narrowing of the rivers indicated that the peak was not far from them.

Myllada whispered, ``Varpiss Island,'' -- no relation with liquid waste -- ``I read about it.''

\centeredstars

They reached the peak, a plateau with a fountain of pale blue stone -- the source of the bright liquid.

Opening her bag, Myllada knelt to the west of the fountain and fished the book.

\q{
	Varpiss Island: located halfway through the Ardssa River; forty \emph{navso} southeast of Enmanteten. Formerly a volcano relocated by Mevaneltes Agerne. At the top, a fountain spews \emph{moevero} -- a glowing, purple liquid whose interactions with other materials has been largely undiscovered.
	
	The island was formerly used as a fortress by the Order of the Birch-Leaf, but in the year 1304 it was forsaken. More recently, however, it became occupied by [redacted] --
}

``We need to leave!''

Lightning struck the center of the fountain, causing it to gush out the liquid and overflow the minuscule streams. The clouds danced as Myllada and Telto hopped the rest of the diameter.

Then drops pattered onto the ground. Myllada lowered her head, clutching her bag to her chest, heading straight toward the canopy of the trees, ignoring the searing pain of the occasional raindrop.

``\emph{Moevero!}'' shouted Telto, also running for her life. ``It's \emph{emveoro} -- poison -- scrambled!''

``That explains it!'' Myllada jumped under the trees in time, a few seconds before Telto.

From a distance, a voice could be heard. ``Who was that? What do they want?''

Another: ``Methinks they spattered unclean blood on this land.''

Myllada could discern two tall figures, completely unaffected by the rain.

The first: ``The rain will have washed the bl'mud anyway. They ran that way.''

Before they knew it, Telto and Myllada reached the shore.

``Where do we go from here?'' asked Telto frantically. ``Swim?''

``In \emph{that} river, and with my books?''

Telto jumped into the violent current. ``Your bag's waterproof!''

Myllada suddenly found herself flying through the air, enjoying the scenic view of the river but dreading the landing; Telto was not far behind her. In a sudden flash of inspiration, she unwrapped the blanket and handed Telto a \emph{meona}. ``This might be our last snack!''

Dead fish flopped from the sky, and what food remained in the sack tumbled to the ground, on the forest floor to be enjoyed by the animals afterwards.

\centeredstars

Back at Varpiss Island, the first to appear seemed disillusioned. ``Is that all thou could'st do?''

``I do not know.''

``Thou imbecile, didst thou know who that person was?''

\centeredstars

A bewitching aura stirred through Myllada's hair. She found herself in a windowless bedroom with stone-brick walls, lit by fluorescent lights from the ceiling. Four paintings were scattered across the room, and she thought she saw parts of them moving. \emph{It was they; I know that act. Lucky to still live. Apparently they didn't know my origins either.}

Telto was still asleep in the bed next to hers. Although Myllada was hungry, she felt as if here were the most suitable place to recuperate.

\chapter{The Sealed Esoteric Laboratory}

When Telto woke up, she found herself in different clothes, and her stomach purred.

``We almost \emph{died}! What the hell were you thinking?'' \emph{So much for having only one fear.}

``Hey, relax. We're on the other side of the river now, and we're in a nice place.''

``Well, if we were dead, then I'd beat you over until we resurrected! We shouldn't even have entered Varpiss Island in the first place. After all, you could have asked your dragon to fly to a different one, right?''

The door opened, and a person with long, sky-blue hair and a navy coat, wearing glasses, barged inside. ``Actually, due to erosion, there are no other islands in that river. Varpiss Island remains only because it was moved to its current location relatively recently.

``There's also a reason that the \emph{Eltesa Ardan} feared crossing the rest of the river. Long ago, Narantar walked over to the river to avenge his master's death, and nearly slew the dragon, but fortunately for her, she sank back into the water in time.''

Telto, surprised, asked, ``How do you know that much?''

Myllada added, ``And what is your name?''

``Arcame Dernar, master of the Magic Snow Castle, and I happened to read about the river.''

``As usual, Darmjarel Telto --''

``-- and Cytaen Myllada, but find another name to call me.''

To which Telto answered, ``Find another name yourself, you lazy grass-hair!''

``That's a beautiful name, though.''

``I agree, Myllada; you should keep it!''

``\emph{Stop!}'' shrieked Myllada. ``I don't want to keep it.''

``Hey,'' offered Telto, ``I bet you can't find a nickname by the end of the day. Loser gets an extra punch in the face.''

``I'd \emph{love} to punch you in the face.''

``Just aim away from the eyes.''

``Well,'' interrupted Dernar, ``wouldn't you like to sing with me?''

``Actually, we're hungry.''

\centeredstars

The dining room carried around sixty tables and had a floor made of wooden planks. Tall windows scattered the walls, taking in the strengthening sunlight.

On Myllada's plate was a mix of fresh vegetables, a fried fish, and a piece of the \emph{amana} fruit. At the same table, her friend and the keeper of the place sat.

``You seem to have landed badly. Did you break any bones?''

``Eh, I doubt it.''

``If you feel that you can walk, feel free to navigate this place yourself.''

\centeredstars

Myllada entered the great library, flooded with sunlight. As in the legend, the bookshelves towered like the trees of a forest, and the ground between them received relatively little light.

The center circle, however, was open. At a table sat a person with long, pink hair, wearing a pointed hat and a maroon coat, behind a stack of books.

Glancing at the books on the shelves as she passed, Myllada approached the focus.

The other, hearing the footsteps, decided to ignore them.

At arriving at the table, Myllada noticed that the person seemed to be working, and decided that distraction was not a good idea. Therefore, she leaned on one of the bookshelves, observing that person from a distance.

It took only a short time before the person noticed another sitting on the floor.

``Hey, I'm only doing light reading right now.''

Myllada approached the one at the table and took another chair.

``Are you new here?'' continued that person.

``I came here only last night. Not exactly a soft landing, either. What do you do?''

``I am Erynor Cjanden, the librarian here. I read here, but I also keep track of the books and answer questions about them.''

While Myllada desired to read more books, she also wanted to, if the story was real, tour the rest of the edifice. ``I'd like to reply with a name, but I've yet to find one, so I'll come back later.''

\centeredstars

As Myllada opened the door, she could feel a warm, arenose breeze. Braziers lit the sandstone walls, now slightly worn, and the tables were littered with papers and various powders, herbs, and solutions.

``Hello,'' greeted one with light red hair and catlike ears. ``I usually have students in this room, but I don't have any today. But feel free to come as one some other day.''

``Thank you.'' Myllada jogged to the next door, behind which lay a dark, musty canal.

\centeredstars

There was no boat anywhere. \emph{Have to swim, I guess.} Checking if her bag was truly waterproof, Myllada set aside the book and the papers and submerged the bag into the water. Surprisingly, when she fished out the bag, the insides were completely dry. \emph{She was right.}

Suddenly, Myllada felt something clasping her leg -- something pulling her underwater. She tried to swim and stay afloat, but that thing was dragging her body down -- tighter and tighter. Under the surface, she couldn't breathe; water was entering her lungs as she gasped for air --

\centeredstars

Profoundly drenched and dripping onto the blue-green grass, Myllada raised her head, locating herself in the celestial garden beyond the boxy river. \emph{I swam only one \emph{navsa}; how am I already here?}

``Ah, you've died and come back alive, carried here by a spell. The residents of the canal often drown swimmers, so we've felt the need to cast it there.''

``So am I alive or dead?''

``It's not the case that you were never dead, but right now, you are alive.''

``And how long have I been dead?''

``The spell takes effect in only a few seconds.''

Shivering and still soaked, Myllada lifted herself. The garden was as described in the story: extraterrestrial flowers blossomed in the edges, and the glass walls, reinforced with a metal frame, separated the interior from the endless void of the rainbow-colored stars.

A mechanical-looking door existed at the end, and before it was a blue circle with patterns traced in gold -- a flowerlike drawing surrounded by writing.

The apparent master of this area wore an oversized leaf as a hat and a pea-green robe with depictions of leaves at the edges. ``Where did you come from?''

``I swam -- or \emph{tried} to swim -- across the canal.''

``I meant: how did you get to the castle?''

``Rode a dragon to Varpiss Island and two people catapulted me off there.''

``Wait... you rode a dragon? Did you tame the \emph{Eltesa Ardan}, the River Dragon?''

``Apparently, I've managed it.''

``That's known to be a difficult feat. How did you manage it, then?''

``Is it sufficient to say that I just threw a fish and let her catch it?''

``It's not just throwing fish; it's something else.''

``Look, we had no weapons that could pierce her scales. What else was I supposed to do?''

The apparent master paused a few seconds before asking, ``What is your name?''

``Well, I'll tell you when I make one up.''

``Do you have no name, or are you just reluctant to tell me?''

``Reluctant.''

``If you've been welcomed by Master Arcame, then I'd be ejected from this place if I sent you back home, and if I don't have this place, then where am I to live? Your secret is safe.''

``Then my real name is Cytaen Myllada.''

``Hello, I am Genreto Narendani. And your parents' surnames are Cytaen and what?''

``Cytaen and Nasrelten.''

``Nasrelten? So you're one of the descendants from an order of dragon-tamers. The slayer Narantar was too, a descendant of one of the order's founders, though nearer than you. I also infer that you are a pure-blood who ran away from home, is that correct?''

``That is correct.''

``Don't tell your parents about me, either!''

``I would \emph{never}!''

``Well, welcome to the Castle of Magic Snow.''

``Thank you. Could you please open that door at the end?''

While walking toward the door, Narendani ranted, ``I'd like to do so, but I've never been able to open it. I found the key, and it fits and turns, but the door never even opens.''

Myllada leaned against one of the side posts, and out of nowhere, the halves split and retreated to the side. ``Whoa, what happened?!''

Myllada flipped the light switch, and the lights worked as they did when the room was last in use a decade ago. The now-uncovered room, with a floor still swept and tidy, held desks with a variety of machines, tools, papers, and terminals. Myllada grabbed a chair and pulled herself to a desk with a gargantuan monitor.

Narendani pointed to a red button. ``I think you need to press that.''

Upon pressing that button, the monitor burst into a glow, displaying a warm \emph{Welcome} and asked for a login, whatever that was. Myllada tried to type in random words, to no avail.

Running back, Narendani carried a note. ``I think someone left this for you.''

\q{
	I have left this facility in 1508 and left the laboratory in the state it was. Please be safe and wear proper protection, and \emph{do not mess around.} In addition, it will be necessary to study science extensively before starting any work; please consult the library for relevant texts.
	
	To log into the terminal, input \texttt{resanal} for the username and \texttt{23h1A0fb69} for the password. You will find instructions for many of the inventions on the computer, in the directory \texttt{\~{}/device-usage}.
	
	P.~S.~if you are still wondering how the lock works, one of the lighted dots on the right pillar is actually a camera that detects a specific shade of purple.
}

Upon reading the note, Myllada commented, ``Well, we'd better not touch anything without knowing what they do. She typed in the username and password, and the computer displayed a prompt. After frustratingly typing random words, she gave up. ``I don't have any idea how to use this.'' She turned off the machine, flipped the light switch again, and, sighing and lowering her head, stepped out of the room, proceeding back to the library.

\centeredstars

By the time Myllada returned to the library, the heat in the sandstone room had dried her clothes.

``Welcome back,'' greeted Cjanden. ``Where did you go?''

``To that garden in space.''

``Did you mean you crossed the canal?''

``Well, I kind of drowned on the way... I also managed to open the door to a laboratory. Strangest lock ever: it detected a specific shade of purple. I think my hair activated it.'' Myllada walked away, searching for an interesting book to read. Between the shelves, she encountered her old friend.

``Where were you?'' asked Telto, surprised at her sudden appearance.

``I'll show you later. But now I'm looking for books.''

\chapter{Not to Deliver, But to Locate}

The old lady Cytaen wept, head on table, lamenting her elder daughter's disappearance, worrying about her demise.

The old man, sitting across his spouse, was now used to the daily pandemonium, the gap at the table, but he was not prepared to let her go. At least until she was sixteen, she could not pass the border to the outside world.

The only trace of the escape was the broken amulet and the severed hair near an opening made by cutting some of the wrought-iron bars. Any person who created that opening must have had access to special tools -- capable of melting iron or exerting enough force.

Of course, it was not feasible to repair the fence, either.

And when Myllada was ill... Could that have been from the rain -- could she have gone outside for the night?

The old man then recalled the note. \emph{Perhaps I have erred, in implying that she had no value.}

But would she take an apology? Was it even moral to prevent her from chasing her ambitions?

Of course not, but it is even less right for a woman to do that sort of thing. To do nothing in this case would be to want a century in hell.

There was a knock on the door.

The old man walked out of the dining room, through the corridors, toward the front door.

``Hello, Senanpros!'' exclaimed the visitor.

``Good evening, Acrynevon! What brings thee here?'' interrogated the old man as he let the visitor inside.

``I was observing Varpiss Island, when I saw two young girls running around. At first, they seemed like visitors from anywhere else, and I triggered the clouds. After chasing them into the woods lower on the island, I launched them from the shore -- but alas! -- it was too late until I realized my mistake.''

``Thou mindless, unobservant goat! Why dost thou visit here? I would prefer if thou hast not squandered my time; squander no more and smell the manure outside!''

``I apologize; I came here not to return your daughter, but to tell you that she has crossed the Ardssa River.'' Acrynevon promptly walked out of the front door, humiliated by the old man's insults.

\chapter{The One-Against-a-Thousand Battle}

It was now winter, and Myllada glanced at the first snow. Despite spending most of her waking hours studying the science (mostly physics and chemistry) that intrigued her, she still struggled with the subject and had much left before she were to be familiar with the laboratory. At some point, Cjanden, tired of answering the multitude of questions from Myllada, started telling her to ``fuck off''.

In spite of her difficulties in her studies, Myllada did manage to construct a wooden trebuchet three \emph{avanto} tall and learned to work with the terminal, well enough to read the previous scientist's comments on the equipment.

Telto, on the other hand, while making the occasional visit to the library for pleasure reading, was more anxious to leave the castle and encounter more places, and had little interest in what Myllada, whom she had learned to call ``Vija'' (wrench), was doing in the lab. She spent most of the day lazing around, occasionally singing with Dernar.

Dernar, however, started shedding tears at times, and Telto found her sleeping more often and eating less, to the point that the latter had to deliver food to her room.

\centeredstars

As Myllada rolled her trebuchet to a lookout balcony on the north (as such a large thing could fit through that path), Narendani carried wheelbarrows of \emph{natan} fruit -- twenty \emph{ceanto} in diameter, covered in spikes, and filled with purplish juice.

Across the wall, snow covered the ground and the crowns of trees, although Varpiss Island was somehow free of snow. The Ardssa River, always rushing, day and night, was, of course, still liquid.

Meanwhile, Cjanden led a crowd, eager to watch the launch. While Telto was a member, Dernar, to her disappointment, wished not to attend.

``Why are we here?''

``What is this?''

While Myllada loaded one of the fruit, Cjanden tried to convince the crowd to stay. ``I think she built this herself.''

Myllada pulled a lever, and the fruit jumped and flew into the distance, toward the Ardssa River, disappearing from view.

``Do you think it landed in the river or on the island?''

\centeredstars

Desperate to capture the old man Nasrelten Senanpros's daughter and regain his honor, Acrynevon rose from the south bank, beaten by the waves and soaked all the way inside. ``Now we search in this area.''

Verenon, previously with Acrynevon on Varpiss Island, followed him. ``What was in the air? It seemed to come from that castle.''

``Let us check there first.''

\centeredstars

``Hey, I see someone!''

Myllada answered, ``Really? Who are they?''

A person ran up, holding a telescope. ``Use this.''

Peering into the telescope, Myllada spotted two familiar beings in a clearing, fresh from the river. \emph{Were those the people I saw on the island?}

Telto reached out from the crowd. ``Let me take a look!''

Myllada gave her the telescope. ``What do you see?''

``Vija, \emph{those are the people we saw on the island in the spring!} They're coming for the castle!''

``No problem, I can aim at them.'' Myllada loaded another \emph{natan}, adjusted the angle, and pulled the lever again.

Telto lowered the telescope. ``You idiot, you can't just hurl fruit at some people and hope to kill them! They can easily spot and dodge them by a wide margin!''

Ignoring Telto, Myllada loaded another fruit, readjusted the angle, and fired.

\centeredstars

``Another one is coming!''

Acrynevon and Verenon moved out of the way -- or they thought they did.

Luckily, Acrynevon dodged the fruit, but Verenon was hit directly in the head, rendering him unconscious.

``What? Hear me, Verenon! Art thou alive?'' Acrynevon tried repeatedly to wake his partner up, but as he feared another flying \emph{natan}, he was forced to continue to the castle alone.

\centeredstars

Acrynevon, now alone, climbed the iron gate surrounding the castle, when suddenly another fruit came flying, in the vulnerable moment when it was too late to jump off, and he feared his demise as well --

luckily, it seemed that the \emph{natan} was mis-aimed, as it landed several \emph{avanto} to his right. Acrynevon, now depetrified from the relief, continued climbing the fence and hopped into the inner grounds, a vast clearing around the castle, covered entirely in snow.

\centeredstars

By now, it was apparent who was inside the castle grounds. Telto knew that person and his intentions, and therefore announced, ``They're coming for my friend! We need to provide a defense! I will stay at this ledge for observation. The rest of you can retreat.''

\centeredstars

Receded in her laboratory, Myllada, still lacking any magical powers, held a simple, lightweight sword in her hand. \emph{Any intruder will have to know when this door opens or activate it by a mishap.}

\centeredstars

``Open the door or thou wilt be turned into fine sand!'' Acrynevon, covered in wounds, but still alive after various attacks, held Narendani by the neck.

``I -- I am stronger than you think, intruder. I can unleash a wind of leaves at you, or hit you with trees from the starry heavens --''

``Thou canst say the same for me.'' Acrynevon knelt and tore a flower. He cast it against the glass, to Narendani's horror, decimating it into a fine pulp. ``Actually, methinks thou need'st to feel it thyself.''

Narendani felt a strong, quick air-shove into the door, strong enough to break her bones but not enough to quite extinguish her soul. Fearing any more retaliation, she gave in, ``To open the door you need to show the right color to one of the lit dots on the pillars.''

``That answer is useless.''

As Myllada heard that worrying comment, she decided to open the door and stab the offender before he noticed. She pressed the button and lunged her sword but found herself launched at a high speed --

\centeredstars

When Myllada regained consciousness, she found herself dropped on the carpeted floor of a hallway, a trail of blood behind her, and she could hardly raise her limbs. Around her, flashes of light crossed each other in a chaotic disarray, with paintings dropped to the floor and doors left half-open, waking her up and infusing the energy she had left into her body. Still shedding a trickle of blood, she ran to a random door and entered the room, slamming the door behind.

In the corridor, Cjanden ducked behind a vase, extending her wand around the corner, firing green bolts with the hope to land a hit.

However, Acrynevon, accumulating wounds over his skin and appearing more grotesque every second, was not searching stochastically, but rather following a clear path, as if he had a destination in mind.

Cjanden showed herself in front of the vase, following Acrynevon and carrying an intricate silver shield that was dropped during battle.

The bloody intruder decisively approached a door and yanked the handle, tearing it off the hinge.

But with Acrynevon flooded a few sixteen wizards, shielding Myllada from his grasp, and yet --

Unexpectedly, Acrynevon drew a long sword and knelt, raising the blade and shoving it through his clothing --

``Your necklace!'' Cjanden leaped toward Myllada, while observing the suicide. ``He put a tracking charm on you -- if he is dead, then so are you.''

Myllada dug and found a short blade on a table nearby, and sawed the amulet --

and Acrynevon rose in anguish, finally dropping onto the floor. Cjanden took his sword and severed his head for good measure.

The corridor, from start to end, was drenched in scarlet blood, dripping from the walls and soaking the carpets, from bodies laying fetidly -- the souls detached from their vessels. Only the occasional bolt or spark sprang from those unaware that the skirmish had ended.

Cjanden, hands stained in blood, knelt before the corpse. ``If one person alone could take two hundred of us, I fear an attack from a more significant part of their association.  They pursue \emph{you}, and if they know that you reside here, then the existence of this edifice is imperiled. Your secret is safe with me, but you must leave immediately -- not from your own faults, but for our lives.

``You and your friend are to depart as soon as possible, covering yourselves up in order to avoid revealing your identities. Exit not from the front gate -- as a murderer stands in the way -- but down the stairs from the armory.'' Cjanden removed a small flask from one of the pockets and opened the lid, forcing the colorless liquid down her throat.

\chapter{A Departure Through Another's Fault}

Not more than an hour after the death of Arcynevon, Myllada walked through the laboratory another time. Other than the chair, which was knocked, nothing has been touched that day. She noted a door, wondering what was behind it, and turned the knob.

It was not a large room or any sort of hallway, but rather a storeroom, but what interested Myllada were the contents. \emph{Those high-tech weapons... If I've known of them earlier, I'd have been able to defeat the man overwhelmingly.}

``Hey, come on! Dernar is waiting!''

Myllada grabbed a few small devices. ``Sure, I'm coming!''

Back at Myllada and Telto's bedroom, Dernar remarked, ``Thank you for coming. We want to get you out as quickly as possible.''

Neither Myllada nor Telto knew how to respond.

Dernar continued, ``Vija, your bag is too small for a long-term vacation. Put this one on your back; it can hold what you need before you leave. I've put in some spare clothes and your papers, as well as food and coins.''

``Thank you very much.''

``I've laid your clothes on your bed, and I'll be waiting for you in the dining room.''

\centeredstars

Myllada stepped into the dining room, carrying her backpack (holding what high-tech weapons she could fit inside) and wearing long boots and a loose, thick, olive-green robe with a hood that almost completely obscured her hair, which she cut again, this time to six \emph{ceanto}. Over her hands, she wore leather gloves with woolen insides, matching her outfit. Telto trailed close behind, in dark orange with a wide-brimmed hat.

``Thank you for your swiftness.'' Dernar crossed the dining room and entered a narrow passage about five \veti{} long, the other two accompanying her.

At the other end was, as predicted, the armory, a windowless, stone-brick room lit only by magic torches.

Telto, eyes lit up, approached a sword and held it in her hand, stroking it gently.

``I'm sorry, but I can't allow you to carry that. You're going to have to use something you can conceal.''

Myllada added, ``How about one of those small daggers -- they're easy enough to hide in your bag and useful even if you don't want to kill humans.''

``That works too.'' Telto picked up two sheathed knives and handed one to Myllada, stashing the other in her own bag.

Dernar started walking toward a tunnel opposite to the entrance. ``That should be sufficient.''

It took fifty steps to reach the bottom of the stairs, their stone surfaces uneven that Myllada feared tripping and falling on each step. The dim hallway, dripping with water, measured nine \eletyn.

``At the other end is an exit in the nearby village. Avoid going north or south. To the east, you will find the border to the outside world, but you will not be able to leave until you have turned sixteen. Therefore, I would advise traveling west.''

``Well, it's been a nice stay here while it lasted. When, or if, I can visit again, I will return.''

Walking steadily across the final corridor, Myllada hoped to see and discover new landmarks, people, and artifacts; Telto was also relieved to travel farther away.

\chapter{The Curse from the Drowned Writer}

They exited to a crowded village under the winter sun, noticing that the exit was well-hidden, a nice distance from the denser parts. In the past days, the roads of the village were still made of dirt and became muddy when it rained or snowed, but within the last sixty years, the people helped pave all of them. Diligently swept, there was little trace of snow on the bricks, arranged in intricate patterns.

As they walked across a road, Myllada spotted a sign: \emph{Sarynde Bookstore}, and promptly changed her direction.

Only when they were inside, the door closed, did Telto gripe: ``Come on! We have to leave quickly; we can't let anyone find us!''

Myllada hesitated before answering, ``It's sometimes going to be dull when we travel. I'm just finding some light reading.'' After searching the shelves for an interesting book, she picked one off, flipped through it, and went to the counter.

``So you've come to buy a book,'' the clerk sighed. ``Not enough people read these days, and even fewer buy here. That's four and a half \emph{mearo} for you.''

Myllada opened her backpack and handed some coins, which the clerk quickly counted and deposited into a box behind the counter.

\centeredstars

Not far outside of the village, Myllada slowed down to a walking pace and panted, feeling a small fire inside despite the harsh winter air.

Telto, still looking as if she could run another \emph{navsa}, was beginning to catch up to her. ``You know, I could run all day without having to stop.''

``I see.''

The path turned into dirt, as if they were traveling backwards in time. During the summer months, the foliage would folded over until it blotted out half of the sun, but as the leaves had fallen, the sunlight still lit the ground vividly.

Myllada carried on, ``So all we need to do is to keep walking until the sun sets.''

``Yep, I'm not feeling even slightly tired. You, however, have already deceived by agreeing to that.''

``Well, if I want to keep up as you do, I'll have to practice walking all day.''

``Good point, but you're not going to become a proficient runner like me overnight.''

Myllada then diverged from the path and squatted, reading thin, hand-engraved characters on a slab of slate propped upright.

\q{
	Caution, Visitor!
	
	The area beyond this point is CURSED; misfortune comes to whoever passes this point.
	
	Turn back NOW if you wish to live.
}

``I don't think it's a good idea to proceed,'' remarked Telto.

``I am not a superstitious person. Someone probably put the sign up to deter looters from stealing from some tomb. Besides, whoever would want to catch us would probably be scared and heed the warning.''

``In that case, let's just keep walking. Or run as fast as we can.''

Myllada bolted off, and Telto followed, although she was kind enough to run only as fast as her friend could.

\centeredstars

Telto, now close ahead of Myllada, stopped at a fork in the path, with both branches appearing identical -- lightened by the bare tree-arms, without any landmarks within viewing distance. She could not see any signs nearby, ancient or modern, in the area. ``I think here would be a good resting-place.''

``It's yet to be the end of the day. We still have to keep walking.''

``But which way?''

Myllada opened her backpack and fished out a small bronze coin. ``If it reveals the sun, then we go left; if it's the tree, then we go right.''

``I dissent. Let us go right if it's the sun, and left if it's the tree.''

``Why don't we flip another coin --''

``The sun, and we flip to your tastes, and the tree to mine. Wasn't that easy?''

Myllada made the first flip, and the coin landed, revealing the tree. ``Sure thing, now it's your flip.''

Again, the coin landed tree up. ``Well, that means we take the left path.'' Telto, silently cheering her victory, strolled onto the left fork.

\centeredstars

``Hey, look, it's another sign,'' Myllada drew attention to a second slab of the same style.

\q{
	This is your last warning!
	
	Whoever enters the tomb of [illegible] shall perish early.
	
	If you value your life, then continue on the path.
}

``Hell no, I'm entering!'' She ran off the path, through a pristine, derelict garden, and into the doorless entrance to a mossy stone-brick stepped pyramid hoisting a gargantuan lens above the roof, not waiting for her friend to trail her.

While from the exterior the tomb appeared unlit, the floors were covered in a sort of radiant, yellowish stone, lighting the passageways with a weak but soft light. \emph{Has it been emitting light throughout the tomb's existence?}

Myllada opened her backpack to take out the book and a sheet of paper, as well as a ``pencil'' (``the writing tool for the civilized people'') to trace out a map of the passages through which she had navigated.

Shouldering her backpack, Myllada proceeded through the hallways, tracing lines on the paper as she went.

\centeredstars

After only half an hour, Myllada reached a circular room with a spherical dome depicting a starry night sky wherein the stars seemed to twinkle and glow. The floor displayed the same symbol she saw in the celestial garden, traced in the same glowing material. The walls were carefully laid with glazed aquamarine bricks, their inner surfaces artfully rounded to the room and the mortar joining them spread evenly and neatly, decorated with numerous curtains spanning ceiling to floor. Ropes attached to the walls, the floor, and the ceiling suspended a seamless marble box.

From the diametrically opposite tunnel, a tall, ashen wight, with long, braided hair ornamented with stained-glass beads in constellatory figures, wearing a white dress with lavender trim, exposing her shoulders but cascading down to the floor and flowing like rills of cloth onto the lapis lazuli floor, curiously refracting the floor-lights. Without opening her long mouth, she trod toward Myllada (frozen by a fascination with her appearance), a lowly passerby in comparison, and uncovered the hood, revealing her short, simple, lavender hair. Lowering her right knee onto the ground and caressing the hair methodically, she formed tears in her eyes, letting them drop and roll over her cheeks, while mumbling in a foreign language.

``I'm sorry,'' whispered Myllada, eyes wide open and reluctant to move. ``I'm sorry, but I don't understand you.''

The ghastly figure, switching to a language Myllada could understand, firmed her tone and slightly raised her voice. ``Ah, have you forgotten how to speak our language? In all those years, you've spoken only \emph{Necarasso Cryssesa}?''

``I've never spoken it.''

``Are you not one of my children, then?''

``I believe not. What is your name?''

``It is Erynor Arato.''

Myllada tried to turn her head away. ``Is Erynor Cjanden one of your children?''

``That is correct.''

``I'm afraid not. My name is Cytaen Myllada.''

``It seems that you do not know about me. I was once an author whose works were well-known, publishing them under another name. Yet the people who respected my opinions were far from all, much less those who agreed with them. In addition, I composed several works in my native language, different from \emph{Necarasso Cryssesa}. As a result, there were those with a reason to take my life, and I hid my true identity.

``Unfortunately, I could not hide it forever, and one night, a band, shouting about having only one god, tied me onto a boulder and cast it into the \emph{Creteavcessa}, the Slithering Lake.

``After my death, one of my children revealed my identity, and raised money to build this monument.''

``How many deities do you worship?''

As if Myllada asked if she breathed, Arato paused and contended, ``No more and no fewer: four. Now what is your story?''

Myllada began slowly. ``I was born in a wealthy family, but my parents never sent me to school, as they didn't want me to know too much, so they could have me perform housework and marry me young. In the spring, I secretly encountered and had conversations with a night-runner (who stands outside of this tomb right now), planning an escape.

``Not long after meeting this person, I went outside in the rain and fell ill the next day, being bathed during the afternoon, to prepare for an event.

``It took two hours after the arrival to the festival to realize that my parents were actually attempting to wed me tonight. I ran into some bushes and hid in a hole, waiting until it was too late to stay outside home.

``That same night, after being scolded by my exhausted parents, I gathered supplies for my departure and jumped out onto the ground from my bedroom, severing the tracking charm placed on my neck and cutting my tresses before running to my friend's house.

``We scared her parents, but they still welcomed us, preparing an early morning meal, but had to leave by sunrise.

``The following day, we encountered a vicious river, foaming blue and white, too swiftly for swimming. We waited a day to gather supplies, but the next day, a river dragon came out of the water and lunged at us. Out of a rush of blood, I threw some of the fish for her to catch, and it returned more slowly.

``The dragon carried us halfway through the river, but as she was too scared to pass Varpiss Island, we had to plan out the second half ourselves. Or we \emph{thought}. Two guards on the island spotted us, unleashing a caustic rain. We escaped in time, albeit holes in our clothes, yet still without a way off the island. Or, again, we \emph{thought}, as one of them launched us into the air.

``Thanks to a blanket, we didn't land too quickly, but the landing knocked us unconscious. We found ourselves in a bedroom in the Castle of Magic Snow, arguing as soon as my friend woke up again. The master of the castle interrupted and told us about Varpiss Island and the dragon before sending us off to morning meals. After finishing, I wandered into the library and explored the castle for a bit.

``Nine months later, we gathered outside on a castle ledge for a trebuchet festival. After launching a \emph{natan} into the river, one of the viewers shouted about seeing someone approaching. The friend confirmed them as the same Varpiss Island guards that we spotted three hundred days ago. I aimed the trebuchet and fired a couple more fruits, hitting one of them directly.

``On seeing the one remaining climb over the gate and land on the other side, all but one of us receded; I ran back to the laboratory that I had discovered nine months past.

``An hour later, I saw the intruder slamming the door to the garden open, with only one more door separating him from me, arguing with the keeper of the celestial garden, Genreto Narendani -- asking her how to unlock the door.

``As soon as I believed that he would deal the killing blow, I opened the door on my side and lunged with a sword, but I felt a shock on my head, and remembered nothing from then on, until I found myself, covered in blood, in one of the castle's hallways.

``I crawled into a room with a lamp on a table and a bed, and sat on the floor, leaning against a wall. Zaps and screams, muffled only by the walls, still echoed in the halls.

``That same man tore the door, as if he knew where I was.

``Apparently, he did, as there was another tracking charm around my neck. Luckily, there was a knife on the table nearby, saving me as he slit his stomach.

``It was no longer safe to stay, so my friend and I traveled to the village to the east from here, destined to travel westwards. We continued to walk, nonstop, until we reached a fork, and two coin flips later, decided to take the left path.''

Arato stood up. ``Thank you for visiting and comforting me. However, since you have ignored the warnings on the signposts, I am obligated to curse you and your friend.''

``I didn't steal anything --''

Ignoring Myllada's plea, Arato rambled in her native language, each second more loudly, while in fear Myllada took an exit.

\centeredstars

Harboring drops of sweat across her forehead, Myllada sighed and lowered the piece of paper, now useless. The hallways had shifted, creating a completely novel layout. \emph{Remember what you learned from the books. All you have to do is hug the right wall.}

\centeredstars

The sun already set by the time Myllada returned outside.

``Did it really take \emph{that} long?'' questioned Telto.

``It did. The layout changed while I was at the top room.''

``What did you get from there?''

``Only a curse.'' Myllada hoped that Telto would take that as a joke.

\chapter{The Sealed Murder Room}

Despite repeated requests from Telto, Myllada vehemently refused to disclose any details about the person she saw inside the tomb, sing-songing ``I'm never telling you!''

Beyond the tomb, the path grew dark as it pierced a small mountain, leaving a tunnel hanging low. The interior, while unlit, felt cozy and warm in midst of the frigid winter.

Telto carried the lantern, lighting the rough stone walls of the tunnel. ``Are you sure you don't want to talk about whoever you met over there?''

``Sure as the stars are distant,'' grumbled Myllada. ``Let that rubbish go and keep walking until we find another interesting place.''

``Come on, what's the problem with telling me?''

``That knife would be useful for slicing your tongue right now.''

\centeredstars

The tunnel, six \eletyn{} long, opened up to a picturesque meadow covered in fields of crops and a small, quiet village. Myllada sat down at the west end, admiring the nocturnal vista from a height and swinging her legs rhythmically, as if she had reached a heaven from the highest mountain in the world.

The multitude of stars, most of them nameless, occupied the sky like spilled grains of sand, in a sea of near-blackness that Myllada had not admired in the last three hundred days.

Myllada felt on her shoulder the firm, comforting grasp of her partner, who whispered various prayers.

After reflecting on what had happened from the day they left the house, Telto lifted Myllada by the shoulders, pointing to the village. The steep path from the mountain consisted of loose, coarse dirt, and to avoid tumbling downwards, they had to hug the walls, holding it firmly while cautiously finding a place to grab next. She gently hummed a tune, breaking the pristine silence that previously existed, following the beats in her head.

\centeredstars

The end of the mountain path opened into a grassland -- only the soft, tall grass, delicately bearing the snow, with no clearing or pavement. Telto's hum faded into silence again as she walked forward looking at the village.

Unlike the central town, lively even at night, this village remained completely dark after sunset; it had no paved roads or street lights, nor did any resident remain awake through the night.

Telto folded her body next to a frozen pond not far from the village, stirring her bare feet across the ice, delicately enough to keep it intact. Myllada sat next to her on the verdant grass, with her legs unfolded away and her backpack on her lap.

Telto put her mouth in Myllada's ear and whispered, ``Are you sure you don't want to talk about it?''

Myllada immediately opened her bag, retrieved her knife, and removed the sheath.

Telto crept away. ``I take that back!''

``Good.'' Myllada put the sheath back on and stowed the weapon. She reclined her head onto Telto's lap, once more staring at the stars and connecting them like dots on a paper. \emph{And someday, stars will stop being born, and not long later, every star will go out. If the human race were to survive to that time, then how would life be...}

No howls of wolves, nor songs of birds, nor any footsteps of men -- there was only the rustling of the grass.

\centeredstars

When Telto rose again, the sun was already up, the last remnants of the crimson aura vanishing. The first thing done was caressing Myllada's arms, bringing her to alertness as well.

``If you talk about to tomb one more time, your tongue will be the least of your worries!''

Telto did not respond, instead starting to walk toward the village, now showing signs of liveliness. The gravel paths crunched under her feet as she strolled.

A short, old person noted their distinctive dressing habits. ``Hey, you're not from here, are you?''

Myllada cocked her head. ``What's your problem with \emph{me}? I should get out of here, shouldn't I?''

``I'm sorry; I just wanted to know where you came from.''

``North of here, then.''

``Well, come into my house, wherever you come from.''

Telto, always appreciating another's hospitality, trailed Myllada.

The old person sat on a chair. ``Sorry, this is the only one I have.''

``That's fine.'' Without hesitation, Myllada curled up on the wooden floor, hugging her knees and waving her torso back and forth.

``I'm going to get something for us to eat, and I'll be back in a short time.''

While the old man was away, Telto teased her, ``I bet you told everything that happened from your birth to then in the tomb, in great detail, and, on top of that, twice.''

``That's not what I did,'' refuted Myllada.

``Oh well, I don't want to have to listen to that again, plus the part since you left the tomb. I'm leaving.'' Telto walked out of the door, in search for other, more interesting residents.

``I'm back.'' The resident carried a tray of bread and vegetables. ``Now, tell me more about yourself.''

\centeredstars

``... and this morning we woke up and decided to reveal ourselves.''

``Oh, you could have done that as soon as you'd arrived!''

The old person had been speaking in a higher tone than Myllada anticipated from such a person, in addition to traces of archaism -- not only due to his age (eighty, as he claimed), as even an eighty-year-old would not speak exactly like that. Often times, he unknowingly began words with \emph{co} when they should have begun with \emph{ce}, or \emph{ca} when they should have begun with \emph{cja}, and even \emph{cja} when they should have begun with \emph{ca}; moreover, he occasionally pronounced his ch's and sh's strangely.

``I'm sorry, but I can't let you live.'' Myllada drew and unsheathed her knife, and struck it into the old man's mouth.

The door slammed open, and Telto stomped up the stairs, spotting Myllada holding a bloody knife and a fresh corpse in the corner. Without giving her a chance to speak, she yanked on Myllada's wrist, ran back down with her, and jumped out of the door.

Hiding her hands in her sleeves, Myllada hurried behind Telto until they were about a quarter \emph{navsa} away from the boundaries of the village.

``What have you done?'' interrogated the hot-bodied Telto, softly enough to not be heard. ``What the fuck is wrong with you? You killed an innocent person and now the whole village will be after you!''

Myllada, feeling blood drain from her body, tried to reply, ``That person, I believe, was not innocent. I could hear him fail to resist talking the old way.''

``You've already lost God's love, and mine as well. Do not follow me.'' Telto strolled back east, not turning back.

Disappointed and remorseful, Myllada ran west as the village produced an indistinct noise of those discovering her murder. \emph{Those caves. That's a good place to hide.}

\chapter{Perhaps, Bound to Hell}

Having entered the cave, Myllada sought deeper branches, hoping that no one would find her. As the lantern belonged to her former ally, she stumbled in complete darkness.

However, a dim, red light flickered somewhere, and hoping for a useful item, Myllada followed it, seeking more luminosity.

An obsidian door, two \emph{avantar} across and up, sat at the end of the tunnel. Exhausted from the running, Myllada lay down for a few moments, observing the fiery swirls within the glass. \emph{I probably deserve to go to hell for what I've done.}

Myllada turned the wheel with what little force she could give, at last unsealing the ponderous door, and despondently took a step inside, instantly closing the door back.

The interior, long, helical tunnels lined in brimstone, felt considerably warmer than the dank caves on the other side of the door. The disconsolate child, never ceasing to walk downward, produced the first audible signs of desolation.

\centeredstars

On counting one hundred forty-nine full turns, Myllada, drenched in sweat, arrived into an open space, accompanied by a boisterous chant of hedonists, eating, dancing, and fighting. She walked toward a crystal hut, where a soul remained alone, head on the table, and tickled his sides.

The lone being almost fell out of the chair. ``Who the fuck are you? You look like you've walked all the way from the surface.''

``Indeed, I did come from the surface, hiding after killing an innocent resident of the hamlet near the caves, a crime for which I deserve to spend near an eternity in hell.''

``Do you even know what hell really is? These are only the outskirts. I have been in hell proper for ten years -- a place up to sixty-five thousand degrees hotter than this one, reeking of roasted shit, with a constant bright red tint engraved in your brain. Don't think the outskirts are much better, either. This place is constantly noisy, and one must avoid any rogue fighters, and there is no water to be found at all.

``I, too, have sinned. I spent my entire life with a lazy mind and a selfish heart; I acted unkindly and committed many logical fallacies. Unimportant was God in my previous life, as I worshiped none. My day consisted chiefly of sleeping, eating, and fighting, and after a tragic death, I have spent ten years in hell proper and ten more in the outskirts, with ninety still remaining.

``A murderer such as you would get at least five thousand in the deepest parts of hell. You are still alive, however, and you are not doomed unlike me. Seek forgiveness and apologize; not being loved in the present does not mean losing God's love for eternity, \emph{unless you choose for it to mean that.}

``Do not stay in hell, return to the surface. Not all is lost.'' The figure handed a bronze lantern to Myllada.

\centeredstars

Using the light of the bronze lantern, Myllada crawled up to the surface, greeted by the sunrise of the last day of winter. Kneeling and lowering her head, she started to pray herself. \emph{I have broken your promise by taking another human life, and I deeply remorse my actions. I, then, wish for forgiveness, at any cost.}

Inside her head, she heard a reply: \emph{You have fallen into the darkness, but now you come back into the light. Yet you must repay what you have taken.} The last sound lingered, until it faded altogether.

\emph{What did he mean, give back what I've taken? Perhaps I should give a gift.} Myllada climbed up a high hill, pondering on what to create. \emph{A sculpture, perhaps? Out of stone? I don't have the tools for that? Wood? I don't have anything to use to cut down trees. Clay? I don't have a kiln either.} She lay down next to a pond, drinking the clear water and finding the ability to concentrate to return.

While she continued to recline, two bread-colored rabbits chased each other around a berry bush. Myllada's mind accelerated to full speed. \emph{If I took life, then, according to the reply I have to give life back.}

\chapter{The Mountain's Reflective Sea}

It had been fifty-one days since Myllada last glanced at the village to which she tiredly marched, rabbits on her shoulders and behind her like a long, fluffy tail.

Yet the village was completely empty and the houses flattened to ground level. Only Telto, weeping on one of the porches, remained. ``Is that you, Vija?''

``Yes, it is I, Vija. What has happened.''

``The following day, five of \emph{them} arrived from the north. Most of the residents tried to hide in the basements, but the attackers searched every edifice, killed those inside in cold blood, and set each one on fire. As a result, the entire population became wiped out; only by hiding on a tree did I survive. As grave as a single death is to the victim's peers, it is minute to the extinction of a whole settlement.

``Oh, Vija, if only you were there! I noticed that your backpack contained a weapon that would electrically incapacitate a human being for long enough to saw their head off. If only you were there, so would the rest of us!

``And about the victim... If he really were a traitor and you left him alive, he could have divulged valuable information to your parents. I should have listened to you more closely! Of course, I am guilty of a great sin.''

``I suspected something from him since, at times, he accidentally spoke in an old-fashioned way. I apologize to you as well.''

``Accepted. What happened with you meanwhile?''

``That same night, I stumbled into caves, trying to find my way in complete darkness, when I noticed a weak glow coming from a mysterious door. Out of curiosity, I opened it, noting the spiraling tunnel past it. The tunnel led to the outskirts of hell, where the dead partied continuously.

``I spent less than an hour, speaking with only one person; following his advice, I returned to the surface and asked God to forgive me.

``And during the first half of spring, I went up to the mountains, breeding the rabbits that you see right now.''

Telto, now smiling, was already squatting around the ground, surrounded by a mob of rabbits, smelling of hay, climbing up her body. ``Hey, if there's no one who'll take them, we can just let them go.''

\centeredstars

As Myllada squeezed herself through a narrow pass to the west, the rabbits still tagged along her. ``They just won't go away, will they?''

Telto was about to make a cunning reply, but held her tongue in time. \emph{Maybe they will if you tell them what you encountered inside the grave.} ``Try scaring them away.''

Lowering her body, Myllada growled and roared. The rabbits stirred around, but after a few minutes, they hopped toward her again.

Telto stepped back from Myllada. ``I thought that was pretty scary. Those rabbits are like you. They're not afraid of anything.''

``Well, maybe you can go away and see if they fear me when you're not around.''

\centeredstars

Beyond a point the rabbits dispersed and the slope stopped dropping and only rose; Myllada found it difficult to keep her breath. Now clothed in young green leaves, the trees thinned out, revealing the deep, cloudless sky, a void of blue ether in an earthen pot overgrown with moss and fungal spores. It reminded her of a dream -- one of floating in the air, flying through the vanishing clouds, watching the round Earth, covered in water, and in grass, and in trees, and in ice, and in sand, turn, villages and mountains whizzing past her eyes.

``Watch out!''

Hearing a soft crunch, Myllada felt the ground swish under her like a tablecloth, and a second later, she landed at the bottom of a pit, three \emph{avanto} deep, skewered with sticks, squalling in pain, as if her left leg had been hacked with a shovel.

Telto looked down. ``Are you fine?''

``I think I broke my leg. Do you still have the rope?''

``What the hell do you mean, you left the rope? You were the one to bring it, weren't you?''

``Wait, what? I thought Dernar would have put that in my bag, then. Let me take a look.'' Myllada opened her backpack and sank her hand toward the bottom, touching for anything ropey. Giving a sigh of relief, she slowly pulled out the twine snake, still in good condition.

``It was dumb luck that saved you this time. You should try to be less forgetful.''

Myllada closed her bag and threw the rope to the surface, which Telto subsequently lowered. Using her right leg, she pulled herself onto each knot, finally clasping her arms around Telto's shoulders.

\centeredstars

A day's trek brought Myllada and Telto to a high lake, too large to see one end from the other. Even in the rain, the water was a pure freshwater teal, and most parts of the lake, save the end that connected the Ardssa River, hardly saw even a ripple.

Sitting on the gravel beach with her legs unfolded, Myllada opened her book to the page with maps. ``So this is the Setenyr Lake. Three and a half \emph{navso} across.''

Telto, standing behind Myllada and noticing her map-viewing, interrupted, ``Hey, let me see that map!'' She reached for the book.
(
Myllada obliged. ``I don't even feel like reading anymore. Just make sure to return it in good condition; I don't want to read a wet book later on.''

The book was flipped to the page showing the western part of the Unknown Land. Telto's eyes concentrated to the east of the lake and the (abandoned) village, back at the mysterious forest with its cursed trails. On the southern path, a point was labeled \emph{Grave of Erynor Arato}. She flipped through the pages and stopped on the entry for that person, and began to read. The book was not the dense material anticipated by Telto; the diction was easy to understand; unliterarily clear and simple.

Finished reading, Telto closed the book and walked up to Myllada. ``You can have your book back.''

``Thank you.'' Myllada inserted it into her bag.

``By the way...'' Telto paused momentarily.

``Yes?''

``Did you see a person named Erynor Arato?''

``There seems to be someone who wishes to fuck her corpse.''

Telto, startled at Myllada's salty language, cut off her own speech.

``As if I can't say that word unlike you.''

``I just didn't expect it from your mouth. Do you want to search around this place?''

``That seems to be a fine option.'' Without waiting for Telto, Myllada limped counterclockwise around the lake.

\centeredstars

Seeing Myllada walk more slowly because of her broken leg, Telto breathed heavily in impatience, ready to yell at her to hurry up.

It took the rest of the day until sunset to even walk a quarter turn around the lake. By then, the water rushing in \emph{rytalel} into the snake of water could be heard as faint hisses.

``Okay, it's been a long day for you, wasn't it? We can rest here for the night.'' Telto removed a handful of vegetables and a deep pan with a long handle. ``Collect some wood for the fire, will you?''

Myllada descended into the forest, still limp. Mindlessly gathering sticks and dry leaves, she hummed a tune while Telto made a fire-pit with the grit, propagating circles of disturbance across the reservoir.

``Hope you can find something useful.'' Myllada dumped the pile into the indentation dug in the gravel, by chance not displacing any of the pebbles along the edge.

Telto removed a flint and a bar of magnesium and struck those two together, producing a shower of sparks which ignited the leaves.

As Myllada, sitting on the beach, smelled the ingredients of the stew mishmashing into one and heard the vaporous bubbles pop en masse, she could not help thinking about the derelict village -- a misunderstanding that caused their separation and its demise. \emph{\emph{I} could have prevented that; why wasn't I there? Well, things happen, I guess. Fortunes and misfortunes; times of joy and times of sorrow.} Still, her mouth watered, given that she had not eaten since morning.

\centeredstars

Day broke again, awaking Myllada, who slept lower on the mountain, in the grassy area. Telto, not far away, was still asleep, so the former opened up the book, finding random articles and reading them thoroughly.

When Telto finally arose out of her slumber, Myllada still read. ``Are we going to read all day or are we going to walk?''

``We're obviously not reading all day! I was just waiting for you to wake up.''

``Good. Then lead the way.''

As Myllada dragged her left leg, the sounds of the waterfall tempted her skin; she wanted to run toward it, but obviously could not; instead, she burst out into song:

\s{
	\itshape
	There once was a rabbit who lived in the woods, \\
	And drank from a magic pond -- \\
	Who slept one night, inside the warm ground, \\
	And woke up as a human.
	
	With his hair the color of what was his fur, \\
	And long ears pointing up -- \\
	Garbed in a long black robe, suddenly, \\
	Without knowing from what he was before.
	
	Speaking and thinking, as if he were always \\
	Not a rabbit, but a person -- \\
	Drinking again from the magic pond, \\
	Turning his head around.
	
	``Where do I go, and what do I do? \\
	What can I do with my new form?'' \\
	His long rabbit ears twitched left and right, \\
	His bushy tail up and down.
	\normalfont
}

``That's such a silly song!''

``I just made it up. Here, I have something.'' Myllada, still walking, produced a polished wooden flute and brought it up to her mouth. While she played tunes, Telto continued:

\s{
	\itshape
	He hopped from his home, the forest \\
	Searching for a structure in sight -- \\
	By day, he ran, and by night, he slept, \\
	Though he could not burrow the ground.
	
	Several days passed, and weary, \\
	He found a village in sight. \\
	The roads and houses made of stone; \\
	Traveled by humans, day and night.
	
	He walked by a wide, wide street \\
	Not hiding even his ears -- \\
	The grown people stared; the children laughed; \\
	The rabbit-man feigned not hearing them.
	
	Looking over the boards for the town; \\
	Reading over every notice -- \\
	The rabbit who turned into a man \\
	Decided to visit the bookstore.
	\normalfont
}

Not waiting for Myllada to stop playing her flute, Telto apologized. ``I hope you didn't mind that my rhythm wasn't perfect.''

Myllada put down the flute. ``I'd like to see a half-rabbit half-human, actually.''

``Best you can do is put on fake rabbit ears, of course.''

``Actually, I'm better at making melodies than words for them.'' Myllada resumed her flute-playing, continuing the steady, walking-pace rhythm and the merry tone.

Telto, unsure of how to continue the song, kept listening, without contributing additional lyrics.

\centeredstars

It was late afternoon, and Telto had a flash of creativity.

\s{
	\itshape
	The rabbit entered the bookstore, \\
	Flopping his ears into his hair -- \\
	``If you're still looking for those to work, \\
	Then I would like to do so.''
	
	The shopkeeper, unsure what do say, \\
	replied, ``Why are you here -- \\
	you're a random stranger right? \\
	What do you want from me?''
	
	``I have just come to this village,'' \\
	and his ears sprang back up, \\
	``a week ago having been a rabbit, \\
	living in distant woods.''
	
	The trees, the stars, the sun, the moon, \\
	the sky, the clouds, the rain, \\
	The snow, the sand, the stones with runes, \\
	A great cat with a mane.
	\normalfont	
}

``That last stanza didn't even have anything to do with the rest of the song.''

``I can't pull ideas from thin air forever, can I?''

The waterfall thundered and roared more loudly as they proceeded around the lake.

\s{
	\itshape
	The lake, the cliff, the waterfall, \\
	Into the river wide, \\
	And long, and swift; and not so tall \\
	Nor calm, as I confide.
	\normalfont
}

The waterfall, four \veti{} high, decorated the limestone cliffs, with an occasional courageous tree making a living high up.

``Hey, Miss Afraid-of-Nothing, do you want your name?''

``Er, sure. What do I need to do?''

``It's obvious. You jump down the waterfall.''

Myllada cringed. ``That's idiotic. I have a broken leg.''

``That's great, as long as you want to be called Miss Afraid-of-Jumping-Down-Waterfalls.''

Steaming in anger and envy as well as needing a way to cool down, Myllada jumped off the cliff, dousing herself in the falling mist in a trial of intrepidity and recklessness. Unable to run with her limp leg, she aimed for a small pocket of deep water among the shallow areas.

Walking back to the waterfall, Myllada hollered, ``Hey, I'm not dead yet! If you think you're so strong, why don't \emph{you} try?''

``Sure.'' Telto jumped in another direction while her short hair waved in the wind. Having gained sufficient horizontal speed, she flew across a strip of land, hitting a deep part of the river across and clutching a stray branch in time before getting washed further away along the river.

``That was close.'' Myllada walked across the shallow parts to Telto's side.

``That was more reckless than fearless.'' Telto produced her knife and pulled away the cover. ``Come closer to me. To become a real adventurer, one must bear the marks on one's face.'' She made swift cuts on the skin, drawing a simple pattern on Myllada's face before handing the blade.

``Okay, now it's my turn, right?'' Unlike Telto, Myllada traced a more complex pattern of interlocking curves, forming leaves and branches.

``You did a good job, Vija. But it hurts a bit.''

``You can't even look at your own face right now, though.''

\chapter{The Spring Wind's Return}

Their faces obscured in drying blood, they walked along the bank, a strip of bare dirt hugging the rushing water, adjacent to a short vertical rise into the woods. Near enough to be heard from behind, the waterfall continued to dump its water, aerating it and producing a screen of fresh mist. The last remnants of the sunlight vanished, revealing the multitude of stars in the deep night sky.

A few drops of blood still dripped on Myllada's clothing. ``I think we should explore the rest of the lake. Shall we head back up?''

``Well, you might not be afraid of wolves, but given that they can smell spilled blood, I'd call that foolish.''

``We can wash our faces before going up. Let's camp here.''

\centeredstars

A ``compact railgun'' (which she had never fired, instead having only read the label) in one hand and the dagger in the other, Myllada was wide awake, watching for attackers in order to protect her sleeping partner, while reading to pass the time. The electric lantern sat on the ground, adjacent to Telto, her hat lying on top of her face.

The bushes rattled. Myllada turned toward the source of the sound, her hand gripping the trigger. Holding her feet still, she concentrated on the surroundings, trying to pick up another rattle.

A shadowy figure materialized, stirring the grasses and taking tiny steps toward the shore.

Myllada continued aiming with the gun, but she hesitated to push the trigger, lest she murder another innocuous civilian.

As the figure approached Myllada, its pointed ears became visible, and the lantern lit its face, flanked by coral hair.

``It's you again? What are you doing out here?''

This was Alarysesmala \yronsyncra, the half-cat, half-human. ``I'm here to tell you that it's now safe to return to the castle.''

``I do not believe you. To begin, what are our names?''

``You are Cytaen Myllada and the person sleeping there is Darmjarel Telto.''

``Telto, awake!''

``Why?'' groused Telto. ``It's not morning yet.''

``This cat wants us to return to the castle. Now tell me why I should risk my life and those of your followers?''

``It has been a full year, Vija. They have already looked elsewhere.''

``We already have plans to return to the lake tomorrow morning.''

``Please heed my advice: there is an army waiting there -- an army of two hundred soldiers, each as powerful as two hundred of ours. Those stationed there will, without doubt, mercilessly disfigure and obliterate any lifeform that surfaces there.''

Telto interrupted, ``I, too, don't believe you.''

``Why would I ever lie to you?''

``Perhaps you're an impostor. After all, I can't accept the words of others without proof.''

Myllada brushed her hair off of her bloody face. ``Let us wash our faces now.'' \emph{Perhaps the flute should have stayed in the bag. You seriously fucked up.}

\centeredstars

Remaining on the packed-dirt path, they painstakingly climbed the hill, checking for every stray leaf or stick without the aid of any light save that of the heavenly bodies. They remained on all fours in order to avoid rogue tree-branches until the trees started to thin out. Even this high up, the hill impeded the view of the lake's surroundings.

``Can we get any closer?'' whispered Myllada. She stopped as the density of the foliage became half of what it was at the foot, still too distant to hear what little sound such an army would produce.

``Perhaps a little more, but there isn't much more we can do. There's no way to observe them without triggering their senses. Their existence can be proved only at the cost of one's life.''

``Thanks for wasting my time, then.''

``On the other hand, if you return, then you can check the satellite data for yourself.''

Myllada took the first stride back down, finding a place without a stray leaf or twig for her next step...

\centeredstars

While the descent from the hill happened agonizingly slowly, as any noise would equate to instant death, the run along the river, more distant from the peak of the hill and on softer, quieter soil, happened more quickly. With \yronsyncra{} carrying the broken-legged Myllada on her back, the party reached the forest path along the castle by midday.

``Now do we head for the village?''

``That's far too dangerous; there might be spies tracking our whereabouts. Telto, just follow me and I'll lead you to another entrance.'' \yronsyncra{} accelerated farther along the Ardssa River, which, still powerful enough to wash a wolf away from its family, meandered into lower elevations.

About three \eletyn{} downstream from the forest path, the half-cat slowly lost speed, stopping at a low-hanging cave entrance. ``We'll have to enter. I can't carry you inside, but we'll be going slowly and your broken leg won't matter anyway.'' She lowered Myllada onto the ground and crouched before walking into the chasm.

\centeredstars

The end of the dim, dirt-walled tunnel led to an underground chamber measuring a \emph{veten} and a half from the stone floor, scattered with long rugs, to the arched ceiling, half-painted with ropes delicately hanging wooden scaffolds. The six \emph{etago} it covered was vividly lit with crowns of glowing orbs in the nine colors of the rainbow, projecting an elusive image on the stone.

Telto inquired, ``What's the point of this room? Right now it doesn't seem to have a purpose.''

``It is unfinished. Completing the artwork on the ceilings has taken twelve years so far, and those responsible for carpeting the hall can't stop bickering. However, this is planned to be used as an arena.''

``Guess it would take twelve more to finish painting the ceiling.''

``You should show us how to fight someday.'' Myllada removed her hood, revealing her hair, now grown back to her shoulders.

``The fighting you've seen is no longer how we fight. As the civilized elect to use the pencil as their writing instrument, they elect to clash in a more strategic manner. For today, however, you must bathe and rest.''

\centeredstars

Myllada, recently washed and dressed in soft bed-clothes, flashed her hair at the door camera (acknowledging her interest in the lab, Cjanden provided a boat at the canal) and turned on the lights. Putting on goggles and a lab coat, she smiled as she walked past all of the arcane contraptions, relieved after her long walk and satisfied to return to where she was a quarter year ago.

Adjacent to the laboratory was a modestly-sized bedroom, with a closet spanning one wall and a bed sitting against the opposite. Myllada shut the door and hung her goggles and lab coat before collapsing onto the bed.

\centeredstars

When Myllada rose from her bed, the clock read twelve \emph{eneo} past noon -- after the end of the sunset. \emph{Great, now I'm going to sleep by day and walk by night. Perhaps the cat is still awake?}

\centeredstars

Myllada hopped off of the steel boat, a lantern in her hand, a dot of whiteness illuminating the algae-covered walls and the murky surface of the frigid waters. She opened the tall door, feeling a cloud of warmth and a flood of fiery light.

\yronsyncra{} was sitting behind a sandstone desk, reading a thick book before looking to her sides and finding Myllada standing beside her. ``Good evening.''

``Yes, indeed. Didn't you say you'd teach me the ways of fighting?''

``Ah, never explicitly, but I implied it. Yes, I had plans to do so, but I almost forgot, with several hundred students to teach.''

``Are you busy right now?''

``Well, I got distracted anyway. Evidently, the arena is still under construction, so we can battle in one of the hallways.'' \yronsyncra{} removed her glasses and pulled back her blanketed chair as her ears twitched. She stood and pushed the chair back under the desk before taking a wide gait along the main aisle and toward the door to the library.

Inside the library, Cjanden, her hat dropped from her head, had fallen asleep on a table, surrounded by stacks of books reaching three \emph{avanto}, under the glass dome revealing the night sky, its stars spinning around the pole.

\yronsyncra{} turned right, leading to a comfortably-lit hallway that could fit thirty people abreast. Before walking about a \emph{veten} away, she handed Myllada an unpainted wooden box, engraved with an icon of a bird on one of the large faces and holding a hinge at an edge opposite of the engraved face. One could hardly see or feel its seams along its edges.

Myllada turned the hinge and peered into the box, finding a several dozen cards. She took out a few, feeling them. The cards were sturdy, as if they were made of wood rather than paper. Their backs each had an icon of a branching tree under three stars, but their fronts were distinct, bearing numbers in their descriptions. \emph{Oh my, there's even math involved in fighting nowadays.}

``Okay, now we get to shuffle those cards. Follow as I do.'' \yronsyncra{} repeatedly took out a small section of her deck and inserted it back at the top.

When Myllada followed, she dropped her cards all over the floor. She immediately knelt and picked them up, stacking them front to back, and repeated \yronsyncra's technique until she could perform it with reasonable dexterity.

``Let's start now. We each draw seven cards.''

Myllada looked at the cards in her hand, trying to make sense of the digits and symbols.

``You need those little dots to cast spells. The number you need is shown on the top left corner, okay? I'll let you go first.''

Almost immediately, Myllada displayed a card, using up the dot she had to deal a small amount of damage.

As a bird pecked on \yronsyncra, she replayed a ridiculous laugh in her mind in response to Myllada's foolish action. \emph{Ha, only eighty points? I won't even need to use shields.} She showed back a card, giving herself a scarlet aura that circled around her, but the dot did not vanish. ``That's three-eighths more damage for my next fire attack.''

Another dot materialized in front of Myllada, who drew one more card to reach seven again. \emph{What did she do there? It seems to be a spell that gives more power.} She flicked through her cards, and flipped one toward \yronsyncra. A yellow aura flew out and circled her.

\emph{She's learning fast. Perhaps I need to put on a shield, after all.} \yronsyncra{} fumbled for a card, and on showing it, a sphere of blue, green, and yellow crystal enveloped her.

\emph{According to this card I can break two of her shields for one of these balls. But she already has one more than I do...} ``Screw it, your shields are going down!'' One of her orbs flew in toward \yronsyncra, smashing the yellow and green parts of the sphere.

\yronsyncra{} sneered, \emph{She'll be wasting her pips all day before she gets to attack.} Out of another of her cards launched a white aura into orbit with the red.

Myllada gained another orb, but this one was yellow.

``Oh, I almost forgot to tell you about those. Since your element is wind, you can use these for two each on wind spells.''

\emph{I'll use one to get five-sixteenths more on each element.} Four spirits flew direct up and landed near Myllada, quickly revolving around her.

\yronsyncra{} played the same card, using up one of her own motes as well.

It was Myllada's turn again, and, having gained another yellow one, she summoned a winged swordsman, who absorbed the two yellow auras and slammed the sword on \yronsyncra.

``You'll take forever attacking like a wimp!'' \yronsyncra{} saw a yellow dot in front of her, and using another card, launched a red lens aimed at Myllada. As she saw her opponent deciding on which card to play, she wore an uncanny smile.

Almost instantaneously, Myllada raised a card in the air. Unlike the other auras that ran about \yronsyncra, smooth and round, the one that hopped into orbit was jagged and dark.

Realizing what flew in, \yronsyncra{} stomped her feet and yelled out all of the swear words she knew.

Myllada commented, ``Just pretend I have a third more health, won't you?''

Broken-hearted, the cat, leaving only a white dot behind, summoned a hooded, masked figure with a long tube, who used it in order to blast fire into Myllada's face. Needless to say, that fire only felt slightly warm, rather than the burning sensation of actually catching fire. Yet this single attack deducted almost half of Myllada's health, and it would have been over two-thirds if she had not caused the cat to barrage her with foul language.

Myllada wished that she had a spell to restore her health, but she found none in her hand, let alone the power to cast one. Instead, she cast another shield, this one appearing white.

\centeredstars

After \yronsyncra's first attack, Myllada decided to play more wisely, saving her white and yellow for a more powerful attack and stacking strengthening spells on herself. She finally accumulated seven of them (two yellow ones), and had many colorful spirits flying around her (plus two dark ones, but they would never both affect the same attack), as well as two lenses, aligned and aimed at the cat. \emph{This should be more than enough to knock her down.}

\yronsyncra, too, was about to reach seven, and had set up strengthening spells to damage Myllada as much as she could, but regretted not attacking earlier.

As Myllada raised the final card, her heart beat faster, hoping for something to pop up -- but alas -- the card only showered a few yellow sparks.

``You're out of luck.'' \yronsyncra{} raised her own card, summoning a gargantuan anthropomorphic figure made of molten rock, who swung Myllada up and down, and left and right, and front and back, and the whole way around, almost squeezing her into a pulp and throwing her onto the ground. \yronsyncra{} raised her fist, jumping and cheering, ``I win! I win!''

Myllada felt the pain quickly exiting her body as she lay on the floor, surprised that no more of her bones were broken. ``Don't be hard on me; this is the first time I fought like that.''

``Don't worry. You'll get better at it. I was playing at a lower level than usual, too. You wouldn't have stood a chance if I didn't.''

``Do you want this back? I'd like to study it.''

``This deck was made for demonstrating the basics of combat. Please return it after you're done. It is my duty, however, to provide a starting deck to you, and I will do so.''

\chapter{The Pervasion of Mathematics in Warfare}

Exhausted from the battle, Myllada returned to the library, taking her box of cards. She removed them and spread them face-up across a table, under the light of the magic lanterns hanging from the ceiling. By the next morning, she felt that she could collapse into a pile of cards at any second.

Cjanden lifted her head from the table and drank from the flask of water on her table. ``Have you been researching combat strategies all night?''

``Since midnight, I think.''

``Lots of dedication after your first duel, I say. That's a relatively new method of fighting, but I have a book about it for you if you want. It's written by a former Protector, and I've filled in any changes that happened since it was first written, so don't worry that it may be outdated.''

``Thanks. I'll read it when I wake back up.'' Myllada gathered the cards into one pile and stacked them up. While she entered into a doze, Cjanden walked up to a shelf, picked up a book with a red cover, and lay it on the table.

\centeredstars

Near the afternoon, Myllada exited her nap.

Cjanden was reading a book lying on her table. ``It's almost time for lunch.''

Myllada trailed her into the dining room, thirsty and waiting more for a glass of water or chilled tea than any food. ``Thank you for the reminder.''

``I thought you might have been hungry after all that studying, and I don't want you missing a meal.''

By the time of their arrival, the room was half full, and dishes were already being passed out. Myllada, sitting next to Cjanden, accepted a cup and chugged the liquid down her parched throat.

Not long later, \yronsyncra{} entered an arch and landed next to them. ``Ah, it's Cjanden and Vija! Are you feeling well?''

Myllada's throat still felt sandy. ``I need more water.''

Before she even finished, a servant walked up with a pitcher and filled her glass.

``She's just awoken,'' added Cjanden. ``Fell asleep after looking at all her cards.''

\yronsyncra{} only nodded, listening to Cjanden's rambling while rotating her ears.

Having downed three glasses of water, Myllada felt satisfied enough to lift up a spoonful of food into her mouth. Adapted to scavenging her food for the last hundred days, she almost opened her mouth when it hit her tongue.

``... and when I rose up, I saw Vija sit at an adjacent table, and she seemed exhausted.''

``I'm fine now!'' Myllada lifted more of the food into her mouth, trying from a wide range of platters.

\centeredstars

Myllada skipped ecstatically into the library, though ashamed that she could not sample all of the dishes before her stomach was filled to the brim. The crimson book, only about three hundred pages thick, rested on her table, eager to be read. She flipped the front cover, and started:

\q{
	\emph{Rationale.} Since the beginning of time, man had fought in basic methods -- with sticks and stones, followed by swords, axes, and bows, followed by an array of guns. Even in a magical world, combat was performed brutishly, shedding \emph{rytalel} of blood and concluding myriads of lives.
	
	Hardly any strategy is relevant in this kind of battle; when it is at all, it is so on only a massive scale. Even then, it is an extremely complex and unintuitive subject, requiring a broad range of study.
	
	Moreover, the past methods of combat requires excellent reflexes, encouraging recklessness at the cost of planning.
	
	These drawbacks demand a revised set of edicts for warfare -- a more civilized manner of fighting, as the pencil conquers the pen for its cleaner strokes and ability to be erased. Of course, \emph{revised} misleads; a more relevant term would be \emph{overhauled}.
	
	Note that it was not I alone who invented this style of combat; I would like to thank the others who have tested it and offered suggestions: particularly Erynor Cjanden, Alarysesmala \yronsyncra{}, Teremon Etana, and Trentan Dejon.
}

\emph{Surely he didn't write the first draft in pen?} Myllada, chuckling, continued:

\q{
	\emph{Principles.} The objective of the battle is to defeat all opponents; in this case, this is achieved by lowering their health points to zero.
	
	Formerly, a flip of a coin decided who made the first move. All of the combatants would make their decisions before the team that went first attacked, followed by the second. It turned out that this mechanism gave too much advantage to the team that made the first move each turn; as a result, a temporary measure was adopted wherein each team makes its decisions immediately before putting them into action.
	
	Combat is now purely magical; there are no completely physical attacks. Of course, there must be a source of magic in order to inflict damage. While some people may wish to give alternative names to them, magical power is manifested in motes, which a combatant gains at the beginning of his turn through extraction of the surrounding aura. Even beginners find it possible to hold seven motes at a time; more experienced players are known to hold around twenty.
	
	Sometimes, depending on his expertise, the caster might gain a yellow mote; this type contains more power than a white mote, and for spells without any element, or of an element which he completely masters, they each count as two white motes; for any other element, they count as only one each. (Yellow motes may not be fragmented; if there are only yellow ones and a card of rank one is casted, an entire yellow mote is spent.)
	
	Cards are structural mechanisms to transform these concentrated balls of energy into various spells. The beginning of a combatant's turn allows him to draw cards from his deck until he reaches seven; he may discard any number of cards, but must play at most one.
	
	Some cards draw only from the ambient magical aura and do not cost any motes, but others take a fixed number of motes and therefore can be played only if the combatant has a sufficient quantity. Yet others are avaricious enough to consume all of a combatant's motes; the more motes these cards are fed, the more power they exert. The top-left corner displays the number of motes required to use the card.
	
	The bottom half of the card, by convention, concisely states the effect it has when played.
	
	When a card is played, there is a small chance that it may fail to cast. In that case, the card is discarded as usual, and the next player's turn starts, but no motes are consumed. The chance that a card succeeds is also written.
	
	Combatants will often learn to conjure cards out of thin air as they gain experience, both in general and within a particular element. However, these cards can exist only in the context of a deck.
	
	In addition, decks can only hold a certain number of copies of the same card, as well as a certain number of cards in total. \\
	
	\emph{Elements.} There are four basic elements: wind, earth, water, and fire. Beginners will have complete mastery over one of these four elements.
	
	Those using wind magic frequently boast more efficient mechanisms of harming their foes, and thus inflict great amounts of damage even with relatively brief experience. However, their spells tend to fail to start more often than those of other elements, and they tend to faint more easily.
	
	Those mastering earth are less effective at damaging foes, but they excel in converting magical power into life-force for themselves and their allies. Some high-level combatants have even been known to revive defeated players.
	
	Those who prefer water have found to endure large amounts of damage, but they are even worse with inflicting it than earth wizards. In addition to their monstrous endurance, however, they hold a certain level of craftiness and can easily manipulate the state of play as the current sways the water.
	
	Those who play with fire deal mediocre damage (albeit more than earth or water magicians), but prefer not to inflict one great hit but rather to damage their foes over time.
	
	There are also spells that do not have one of these four elements; this middle element is called \emph{energy}. These spells often affect spells of any element or give a separate effect to the next card of each of the four others.
	
	In addition to the previous five, there are even more secondary elements. In order to even be able to use a spell with such an element, one must have achieved a level far beyond mastery of its parent element. In exchange for the effort required to learn and master a secondary element, however, spells using them hold more power than those of primary elements. Secondary elements can, in turn, lead to tertiary elements, \emph{ad infinitum}. \\
	
	\emph{Attacks.} The simplest type of spell deals an amount of damage to the opponent -- the ratio is approximately 88 points per mote, although it varies between element to element. Furthermore, more powerful attacks will yield a more favorable ratio. While inadequate on their own beyond the most elementary level, attacks are an indispensable part of any deck.
	
	While most attacks affect only one opponent, others attack all of them. Such attacks are useful against many opponents.
	
	Attacks may have side effects, such as placing or breaking damage modifiers or returning a portion of the health back to the caster.
	
	\emph{Amplifiers.} Certain spells unleash one or more energetic spirits that subsequently orbit the caster. These familiars wait for a relevant attack to be cast by whom they orbit, at which point they are absorbed inside, increasing the potency of the attack. Special amplifiers can influence other types of spells, such as healing spells or even other amplifications.
	
	It is important to note that two modifiers (amplifiers, shields, and others) from the same spell will not affect the same attack; instead, only one of them will be used and the other will be available for the next attack. Two modifiers from distinct spells, however, even if they appear identical, will stack.
	
	Other spells summon ``de-amplifiers'', which lower the potency of the target's next attack. They are frequently perceived as nuisances, and using such a card may lose the caster his friends.
	
	\emph{Shields.} These cards construct a magical barrier around the caster, and reduces the damage from the next hit he receives.
	
	As with amplifiers, there are also ``negative shields'' -- these appear as lenses focusing on the target.
	
	It is important to distinguish between whole attacks and hits; outgoing modifiers affect whole attacks, but incoming modifiers; i.~e. those affecting the target of the attack, affect individual hits. A spell that inflicts two hits will be boosted as a whole by a single amplifier, but it will take two of the same shield (one for each hit) to dampen both hits.
	
	\emph{Healing.} Some earth spells restore the health of a combatant on the caster's team. Whether they can bring a defeated player back into play depends on each individual card; those with this ability tend to restore fewer points.
	
	\emph{Shattering and Transferring.} Yet other spells can remove damage modifiers or move them to another combatant. The latter action is frequently associated with the element of water.
	
	\emph{Freezing.} Many spells with the element of ice (a secondary to water) have a chance of freezing the target, preventing him from using a card next turn.
	
	\emph{Element Conversion.} A class of spells with the element of light (a secondary to wind) places a lens that converts a hit of one element to another.
}

``Hey, Vija, what are you doing?'' Telto, glancing at the book, open to a page filled with equations, continued, ``Vija, math and combat don't mix.''

``Perhaps you should learn about card combat too. Go bother the cat if you want to.''

``You're becoming like Cjanden now.'' Telto walked away, looking for the sandstone room.

\q{
	\emph{Damage amplification.} Amplifiers and lenses are stacked multiplicatively; in other words, they add and subtract not to the base damage, but to the amount after accounting for the previous modifiers. For example, given two amplifiers that add three-eighths and one-fourth more damage respectively to the next hit, one might instinctively calculate the amount inflicted relative to the base damage as \formone but it is actually \formtwo
	
	This may seem as an insignificant difference, but when more modifiers activate at one time, the difference between adding the increases and multiplying them grow wider. Another implication is that the amount of damage dealt grows not linearly with experience but exponentially. The greatest amount of damage observed was \iformone{} points, casted by Anasar Fenma, twenty-three days after the summer solstice of the year 1523. The base damage of the attack casted, in contrast, was only 2300 points.
	
	It is theoretically possible to kill a human being by casting a spell in this fashion, but doing so would require \iformtwo{} points within a single attack.
	
	\emph{Acquisition of cards.} New combatants will usually obtain a bundle of basic spells from their masters, as it is generally impossible to gain any cards without already having a few.
	
	One can win a card from an opponent by contest (often with more cards gained from larger hits). It is also possible, for some unknown reason, to find an occasional card from a wild animal.
	
	Moreover, cards are often sold or abandoned by more experienced players who no longer find them useful.
	
	As mentioned before, combatants learn to create certain cards out of nothing when they have reached the necessary level and elemental mastery, in a process called ``skill-learning''. Some learn to craft tangible cards as well. Doing so might create cards that cannot be acquired from skill-learning or even have yet to be discovered, but the process requires a vast amount of prior experience. Erynor Cjanden has written a detailed section about this subject, which will appear later in this book.
}

Myllada looked ahead. The next bunch of pages pertained to more detailed descriptions of elements and individual cards, as well as strategies. \emph{I've done a lot of work already. I'll leave it for tomorrow.} She took the empty box in one hand and shoved the cards into it before closing the lid.

Pushing the chair under the table, she ran back to the sandstone room.

\centeredstars

``Thank you for returning my deck. As promised, here's one for you.'' The box in \yronsyncra's hand, slightly thinner than the first, was made of a darker wood, but bore the same avian icon. ``The cards aren't as powerful as those in the last deck, since I intentionally put in high-level cards in the previous one for the sake of demonstration.''

Myllada reached out both of her hands, letting the box drop firmly onto them. ``Thank you for showing me.''

``Use it wisely; deck boxes aren't exactly the easiest things to build.''

Not long after Myllada ran off, she returned, dragging Telto by the arm.

``Agh -- !'' Telto stumbled onto the polished sandstone floor, directly in front of \yronsyncra's desk. ``What the hell?''

``Perhaps you would like to learn how to fight as well?''

Myllada answered on Telto's behalf, ``Definitely.''

``Vija, what did I tell you about mixing math and fighting?''

``Telto, most of the wizards will not be happy when you unexpectedly stab them,'' warned \yronsyncra. ``This is how most of them prefer to clash.''

``I still think that's a bad idea.''

``For practical purposes, it matters less whether it is a good or bad idea than whether it is customary. And I think you'll find it fun once you try it.''

While still reluctant to start, Telto sighed, ``Sure. If I must, I will.''

Myllada intervened. ``May I watch you?''

``On the condition that you do not speak to either of us during the battle, as dictated in the code of ethics, I will allow it.''

\centeredstars

As Myllada followed Telto and \yronsyncra, Cjanden called, ``Ho!''

``Yes?''

``Did you enjoy that book?''

``Well, I read up to the section about how to get cards, but for now, I'm done reading. I'll continue tomorrow. Was interesting though; the language was a bit old-fashioned but still clear, and I found a lot of useful information. Telto, however, doesn't like the idea. Cjanden, this is clearly a superior way to fight. But I saw many people battling the old way.'' Seeing the other two vanish into a doorway, Myllada started hurrying toward them.

Cjanden followed her. ``If it were not for the Order of the Serpent, that is. They desire to kill off all who are less than pure-blooded, in order to form a world of the pure-blooded. Shrinking the gene pool, that is. Under their eyes, your friend is a part of the plague, a pathogen to be eradicated. Also in danger is the cat accompanying her -- a cross between a cat and a human. They, however, in spite of your alliance with such beings (which I do not condemn), offer you another chance to return to your house, untouched; I will not advise you on whether to accept it.''

``I won't accept it.''

More firmly, Cjanden continued, ``In order to achieve their ambitions, the members will use any means possible. As they do not wish to touch the blood of the impure, they will frequently repel their foes at high speeds. If there were no threat back in the winter, then I would not have permitted you to leave the castle. I also ask you: do not go outside, let alone trebuchet another \emph{natan}.''

Myllada only nodded in agreement. For now, all that she wanted to do was to explore the art of new-warfare.

Cjanden relaxed her tone. ``I'm glad you've agreed. And don't risk your cards for duels either.''

By that time they had caught up to Telto and \yronsyncra{} in the same hallway, appearing exactly the same as before Myllada had her duel with the cat. Cjanden retreated near the side and knelt.

Myllada was about to sit with her legs open, but heard, ``You kneel. Polite to do so when spectating a duel.''

``My apologies.'' Myllada rested her knees.

``Remember, don't talk to them either until it's over.'' Cjanden produced a flask uncannily fitted for one of her pockets, and opened the lid, taking a sip of fruit juice.

Myllada scrutinized the skirmish, as \yronsyncra summoned a ragged black aura that flew to Telto.

``What does that do?'' inquired Telto.

``Weakens your next attack.''

Telto hollered the same swear six times in a row.

Cjanden took another sip from her glass flask. ``Most effective way to get someone to curse.''

``She cursed at me while we were away, too.''

``Bet she never said that word six times in a row, though.''

\chapter{The Struggle for Reagents}

For several dozen days Myllada challenged to a duel whoever had spare time, while at other times she stayed in the library, continuing on the book. Every morning, \yronsyncra{} gifted her another card, sometimes one that she had seen in her deck, and other times one that has never been before. The joy of finding new spells and strategies, to her, was its own kind of exploration.

``I think it's still a bad idea to reduce fights to a math problem.''

``I think you're a math problem. Or you just have a problem with math.''

``Meanwhile, you have a different problem with math. You try to tack it onto every aspect of life.''

``I am not to blame here, Telto. You may curse the soul of the person who came up with this method.''

Telto remained silent and walked away. While Myllada obsessed herself with the esoteric arts, Telto found exhilaration in touring the castle and finding new areas previously unknown to her.

Sitting next to her table, Myllada inspected the card in her hand and flipped it repeatedly. On the front, wide brush strokes, outlined neatly in ink, spiraled into each other. \emph{Three hundred seventy to everyone on the other side.} She shoved it into the box and opened the book to where she last left.

\q{
	\emph{Construction of cards.} A card is a mechanism transforming motes into effects in favor of the caster, fixed on card paper. Crafting one by hand is an extremely tedious endeavor; therefore, the preferred method is to use a machine to imprint the mechanism, as well as to copy the icon on the backside, from another card.
	
	One obvious essential is card paper, a type of stiff, sturdy material with a writable surface. One must cut this paper to a size slightly larger than an actual card before smoothing the edges. A ruler is indispensable for ensuring that the template is trimmed to the correct size. After such a trimming, the template is placed in a precise location on the machine; guides often help place them as well as verify that their size is correct.
	
	Machines also require a fuel -- most frequently an oil extracted from the commonly-found \emph{nemoca} plant -- placed in a glass vessel feeding into a flame. More powerful cards will require more fuel to construct; measuring the amount of fuel consumed allows one to calculate the number of motes needed to cast the card produced.
	
	The properties of the card, such as element, type, and strength, depend on the \emph{drivers} -- the other macerated ingredients, which are inserted into a plate near the top. Upon activating the machine, they will direct energy into the appropriate locations on the template.
	
	After constructing the card, it must be tested. This is as simple as casting the card and inspecting the results, multiple times in order to account for its chance of success as well as any variability in its ability; such experimentation will certainly differ from normal battle.
	
	After testing its functionality, the card must be labeled with the necessary fields. Of course, if the same recipe is followed, then the card will have the same effects, and in that case only a single verification is necessary. Naturally as well, some craftsmen have (illegally) pranked unsuspecting buyers by listing an effect different from a card's actual one.
	
	While it was formerly considered unethical to share card recipes with others, this act has now been accepted more widely. Many wizards, however, still elect to keep theirs a secret. As printing recipes is yet a gray area for some institutions, this book will not do so. However, individual ingredients and their properties will be listed.
}

Myllada sighed and lowered the book. On hopping onto the floor, she walked toward the dining room, which, between meals, had a drink fountain and platters of light snacks set up on the tables. After filling a glass with water and grabbing a handful of berries and crackers, she returned not to the library, but to the sandstone room, and entered the class.

\centeredstars

Many students eagerly left, but Myllada was one of the few who appreciated staying in the room.

After another student farewelled the cat, she looked at Myllada and greeted, ``Hi!''

Myllada froze briefly as if he had lifted his skirt. ``I guess, hello to you too. Could you please wait? I'd like to talk to \yronsyncra.''

``Sure, go ahead.''

Turning to \yronsyncra, Myllada hesitated and inquired, ``Do you know... are you familiar with card crafting?''

``Ah! Cjanden always acts as if it's some complicated, arcane discipline. It's easier than you think, but I'm not willing to hand over the ingredients for free.''

``What do you want me to do, risk my life going outside?''

``Since that's clearly infeasible, I think you could spend the evening hours helping clean this room and a few others.''

Knowing her expertise in housework, Myllada promptly agreed.

``I knew you could help. I'll see you after dinner.''

Myllada turned back at the student.

``So you're interested in card-warfare too?''

``Yes. Was that the point?''

``Glad to hear that we share an interest. My name is Vystasage Cjan.''

``And mine is Cytaen Myllada.''

``I've heard a bit about you; about always being chased. You know, I can go out to gather some reagents, for something in return.''

``Eeh, what do you want, then?''

``What about doing my homework for me?''

``Of course not.''

``No, of course not; that wasn't for real. See me at my room when you can.'' The student handed a folded sheet of paper, which Myllada pocketed.

``Alright, I'll see you after I finish my business with \yronsyncra!''

\centeredstars

Although the cleaning work sapped out most of Myllada's energy, taxing especially on her arms and back, she still skipped ecstatically across the hallways, with a modest amount of reagents already in her bag.

When Myllada opened the door, she found the same student sitting on the bed.

``Hello, Myllada.''

``Please call me Vija.''

``Understood. In return for the supplies I promise, I ask you to make clothing.'' Cjan pulled out from under the bed several rolls of cloth, a long metal ruler, and a basket of needles and thread. ``Wait a moment.'' He walked to a bookshelf and lowered a leather-bound notebook, opening it to a page in the middle. ``These are the designs.''

Myllada inspected the clean but detailed drawings. ``Okay, I think I can do it, but it's going to take a lot of work.''

``I already thought it was. I'll pay accordingly.''

Myllada gathered some sheets of paper, trying to visualize the pieces of cloth she needed to cut. ``I would have preferred if you drew the pieces I needed to cut too. Otherwise, your plans are detailed enough to follow.''

``Thank you for your offer. I will return soon.'' Cjan exited the room.

\centeredstars

Another class began, and Myllada decided to sit at a table with a card constructor. She lay down a few sheets of paper filled with notes from the book and retrieved the ingredients as well.

Cjan pulled a chair to her table, looking at the notes.

``Hi.'' Myllada drew out a few templates (already cut) and mounted one of them onto the center of the machine, as well as a finished card on the side. ``The next thing is to get a fuel,'' she mumbled as she rested a flask of pale yellow oil on the tabletop.

``We haven't reached that step yet.''

``I know.'' Myllada held a knife and chopped the willow leaves into small squares before placing them in a drying-plate and filling it with a shallow layer of water. She connected a bottle of seed oil with powdered charcoal mixed inside to a tube and lit a flame at the other end near the bronze plate.

When the water boiled away completely, she tipped the tube to stop supplying the fuel and extinguish the fire. Doing so left dried willow leaf to be ground with a pestle and mortar.

``Nice, now what kind of spell do I want?''

``I'd say start with attack.''

Myllada shuffled through her notes. ``Attack... that requires ground metal.'' She opened a glass jar filled with metal shavings and scooped some into the mortar, banging the pestle until they were reduced to fine sand.

``By Nerassa, you don't have to grind it like a madman.''

``Well, you can try grinding the metal next time.'' Myllada mixed the powders onto a glass plate mounted near the top of the constructor. She poured some of the \emph{nemoca} oil into a side cup and recorded the initial volume, immediately prior to sparking a flame. A mysterious light beam shone out of the flame, reflected by mirrors and focused on the glass plate and the card.

Cjan took a step back out of his chair, as if he had never seen such a process.''

After a few minutes the beam faded, and the card was engraved with a maze of hair-thin lines on the front, and on the back was the usual tree icon. Myllada, looking at the oil level again and performing a few calculations in her head, concluded, ``This should take only one mote.'' She moved to the other side of the room and raised the card, unleashing a massive bird that fluttered toward Cjan. ``How much damage did that do?''

``I'd say eighty. Try it again.''

After about twenty trials, Myllada sighed, ``I'm pretty sure this is the Wing Flutter spell or something,'' as she observed a drawing of flapping wings appearing and quickly copied all of the statistics from one of her existing cards.

``Every card-crafter has to start from the simplest card.''

\centeredstars

Several days after her first visit with Cjan, Myllada sat in his room, finishing the last stitches and raising a patterned blood-orange garment, constructed in two layers of cloth, with yellower trim, with narrow sleeves and wavy seams, and an elaborate light-red belt joining the divided front.

Cjan received it with both hands. ``Thank you for your time.'' He laid it on a chair and offered several jars, bags, and bottles.

``Thank you for yours, too.''

``You're still going to need more, aren't you?''

``Yes.''

``Come back here tomorrow.''

\chapter{The Illusionary War Records}

By now, Myllada had engaged in duels less often (it didn't help that most of the residents didn't want to engage her anymore), as her interest dropped and moved to seeing what kind of cards she could create. Not only classes, but also her free hours were spent experimenting on the constructor. At other times, she sat at the library reviewing the relevant sections of the book, and at yet other times, she completed odd jobs for more materials.

Cjan saw her lift the second article in the air. ``No classes tomorrow, so I'd prefer that you stay here for some more time.''

``I thought there were classes every day.''

``No one expects you to go to every class, you know, and I'm not just making this up. You can ask any of the instructors around here.''

``Ah, so that's why I sometimes find myself overworked.''

Cjan laughed and pointed to the yellow-green one in spiral motifs, with wider sleeves than the previous and reaching only a bit beyond the knees. ``I hope this isn't too unreasonable, but could you put that on?''

``What? I made this for myself?'' Myllada entered the closet, stripped herself completely, and placed it over her body before returning to the room.

``Now you can wait.'' Cjan returned from the closet and held Myllada's hand toward the bed as he rushed under the blankets and collapsed himself.

Myllada thought of escape plans as she was dragged closer into the platform, feeling a hand stroking her left shoulder and another around her neck, rubbing her hair. While her mind still existed in a scrambled state, the fine fabric of her garb soothed her mind.

``Shall I proceed?''

Genuinely curious of his plans, Myllada nodded, ``Yes. At least until I tell you to stop.'' She ran her fingers through Cjan's hair, noticeably less coarse than her own, and her breaths became more weighted.

\centeredstars

Even the longest nights of the far north in winter eventually faded into daybreak, and the spring was already approaching summer by now.

Surprised to find herself outside her own room upon waking up, Myllada jumped onto the floor and straightened her clothes. Cjan still remained in a profound dream, without plans to attend class. Myllada, on the other hand, felt a duty to attend every one she could, and she entered the closet to change to her normal vestures. After scribbling a note and leaving it on the desk, she promptly exited.

\q{
	I would like to attend classes today. Please provide compensation as soon as possible. -- Vija
}

Long after Myllada departed, Cjan groggily rose out of bed. \emph{Congratulations. You've made it through the whole night without opening.} Noticing the message, he approached the desk and held it in his hand. \emph{Vija, she's studious and hardworking. I don't think I'll ever be like her.}

\centeredstars

``Yes, we expect you to come to class every day.''

Myllada nodded, ``Thanks'', convinced that Cjan had lied to her about classes, but simultaneously disappointed that she would not get away with missing class.

Behind her back, \yronsyncra{} and Narendani clasped each other's hands mechanically.

``Never stops cheering me up,'' grinned Narendani.

``I should probably stop lying about it, though.''

``It's always fun. Maybe you should tell every new student that.''

\yronsyncra shook her ears. ``Myllada isn't a new student, though.''

``Well, she works hard, but what would be the consequences if we told her that we hold classes almost every day just to let students come as they please?''

``Perhaps, next class.''

\centeredstars

``You were wrong, Cjan.''

``Hey, that cat likes to pull that prank on new students. Don't believe everything she says.'' Cjan was still sitting in the dress Myllada had put together, with one of his journals on his lap.

``Anyway, I have some cards to test on you. Could we move to the hallway?''

``Sure thing.'' Cjan opened the door and dashed to the opposite bank of the corridor.

Myllada stood at the same side and raised one of the cards. ``From the measurements, this should cost only one mote!'' A perfectly clear lens appeared on Cjan's side, as well as one on her own.

``Now we have to measure how strong these are.'' Cjan raised another card, filling Myllada's face with a jet of fresh water. ``Well, that seems like one quarter more on the caster's side.''

Myllada picked off a card for testing purposes, launching a bright current of wind that lifted Cjan into the air before dropping him. ``Three quarters for the one on yours.'' She inscribed on the card \emph{+3/4 t in; +1/4 c in}. As she placed the card into her deck, she sneered, ``This will come into great use later. I have another to test; it should take eight.''

Another card raised into the air projected a spinning square on the floor, raising with several hundred snakes attached to its neck an oversized figure that chased Cjan, frozen in horror, and sucked his visage with its numerous heads, finally drawing its knifelike talons from its hands and scratch-knocking him into the limestone wall as the wounds vanished from his tingling face.

``One thousand, three hundred five damage, as I see it, Let's try again.'' Myllada lifted her pencil as Cjan recovered from the crash.

``No, thank you. Try it on someone else.''

Instead of writing directly onto the card, Myllada recorded the effects in a notebook, anticipating some kind of variation in the card's potency. ``Did you read the note I left you this morning?''

``I did.'' Cjan returned to his room and pulled out several neatly labeled vials and jars.

Myllada inserted them into her bag.

``Also, there is legitimately no class tomorrow.''

\emph{Is this an excuse to cuddle again?} ``Really, there isn't?''

``Tomorrow is the first day of summer. They often throw a festival at Armadereyn.''

At those words, Myllada shed a few tears. ``Are you planning to go?''

``I have plans with some of my other peers.''

``Enjoy yourselves, but tonight I need a cuddle.''

``Why not?'' accepted Cjan.

``Let me wash myself first.''

Cjan sat on the bed again, notebook opened to an empty page and a pencil in his hand. While writing whatever came to his mind, he awaited her return.

A half \emph{enean} later, Myllada returned in what Cjan wanted her to put on and rolled into bed.

As Myllada lay next to him, Cjan whispered:

\q{
	Vija ... Vija, ... Vija ...
	
	your mind is strong; your heart is strong
	
	I have heard many anecdotes about you
	
	... a person among persons ...
	
	still stay strong in heart and mind
	
	your dreams have already begun to reach fruition
	
	your nightmares a distant, indistinct past
	
	so let it stay so
	
	keep making your dreams reality
}

Myllada, almost forgetting that the commencement of summer was nigh -- convinced that it was instead mid-winter, walked her fingers across the other's back, shivering even in the warmth of direct togetherness in the midst of the inclement darkness showering down a pure drizzle, with Nature's chorus of myriads of raindrops hitting the ground each second in a symphony of white noise, spilling into streams, into rivers, into oceans, circulating across lands, prolonging the life-force of the trees, the grass, the flowers, the animals, humankind -- or sometimes it cut it short, fraying the severed point into distorted, unnatural shapes; she rested her head on the crossed shoulder as her arduous exhalations decelerated and thickened into a steamy mist, by which time her hands reached the lower parts and in-receded, now producing rhythmic thudlets on the thick material while her free-hanging hair crept around her neck and onto her torso, and her exposed legs coiled around the ones on the opposite end, and only occasionally did one lift the thick quilts to ventilate the underside, and the disconnected chants of praise reverberated in her soft ears under the lavender thickets, free of prickles -- yet -- \emph{all benediction without criticism -- I become demented -- } out of her open mouth did come a voice, at frequencies the other could only whistle and a level of delicacy that could never be dreamed, in random pitches before the notes merged into coherent phrases, ac/decelerating periodically, yet this crooning did not silence her musings; she closed her eyes while tears dropped onto the bed -- \emph{disobeyed parents -- snatched food -- became indolent -- heeded no warnings -- took another's life} -- with little rationality to shut them down; they rained on overdrive, and the cart rolled from peak to valley beyond control -- the pitches wavered, and she saw herself descend into an endless abyss among snowflakes, emblems of a hundred and a half days past, though appearing current -- but \emph{I must keep myself intact; I am a methodical person} -- the notes faded into silence, as with the stroking, and she was bound more snugly as she fell asleep.

\centeredstars

Cjan rose early, stirring Myllada alongside, and before he noticed, she had already jumped out, preparing in the closet. Sitting inside, he waited for her to exit.

``You're up early.''

With only a hurried ``yes'', Myllada rushed out of the room. \emph{Then isn't he too. Quite a weird last night.} Carrying her bag, she brisked through the corridors and the gentle stairs and leaped into the library. She circled the perimeter towards the door to the sandstone room, where \yronsyncra{} was locking the door.

``Good morning, Vija. There is no class today.''

``Are you going outside for today as well?''

``Yes. Do you wish to enter?''

``I would like to.''

``To enter your laboratory?''

``Actually, no.''

``Then I'm afraid I can't leave you alone there. You might want to come to the dining room on the other end; Cjanden plans to provide you and your friend some food in an \emph{enean}. Also, why would I expect you to come here every day? I just hold classes that often to make them less crowded.''

Lonely, with no other diversions in sight, Myllada, having read the crimson book from cover to cover, ambled between the bookshelves, running her eyes and fingers from spine to spine, looking up and down and walking here and across, forward and back, up and down. Most of the books, pertaining to history or literature, felt dry to her brain, but it took only a short moment of haphazard navigation to find one she would enjoy.

This one, with a forest-green cover, bore the title \emph{Records of great card-battles} on the front. Myllada flipped through the pages and returned to the center to lay it down on the table and open the front cover.

\q{
	\emph{Foreword.} The practice of holding magical duels via cards has been dated to as early as 1476 (Teremon 1509) and was intended to reduce fatalities and emphasize strategy over reflexes. Until the rules were first finalized in 1479, however, only those with close ties to the Protector at that time, as well as to high-level magicians, were aware of such a style. Teremon labels this era as the ``foundry period''. Naturally, the battles recorded during this epoch feature unusual mechanics and the effects of some spells differ slightly from those of today.
	
	On the first finalization of the mechanics in 1479, a short pamphlet entitled \emph{The new war} was published within the Unknown Land, particularly in schools of magic. However, the new mechanics failed to receive much popularity in its early years, and many schools banned their distribution.
	
	In order to popularize this practice, advocates, including the original inventors, held public battles, during what is now known as the ``demonstration period''. However, those partaking in such battles were often ridiculed by locals, especially those adapted to real-time combat, and, particularly near schools of magic, they often risked punishment by administrators.
	
	Despite these hurdles, card-combat crept up in exposure and respect during the 1480s, given battles such as that of Engren (1483) and Felgron (1486), which cost almost three thousand lives between them, and praise from a growing organization of instructors and administrators, who formed the Association of Spell Card Advocates (Nedana 1515). By 1472, approximately three out of eight students attending a school of magic for combat purposes preferred such a method. Teremon names the era of rising prevalence the ``first period''.
	
	First period combat mechanics were comparatively simple. They featured only the four primary elements plus energy; moreover, unlike the current practice, all players decided their moves before any player executed them; as the turn order was fixed per battle, this strategy effectuated an overwhelming first-turn advantage. In fact, about twenty-one-thirty-seconds of recorded one-to-one first period battles were won by the player who moved first; similar statistics can be derived from other battles with an equal number of players on each team.
	
	Critics commonly attacked the first-move advantage, but the first to verify its presence and influence came from records of over five hundred controlled battles among similarly-skilled students, which found that the proportion of victories gained by the first-mover was forty-five out of sixty-four (Erynor 1492). In response to this study, the Association promptly submitted a proposal to the Protector (Teremon 1509). Twenty days past, an interim measure became enforced, wherein the decisions would be made on a team-by-team basis; in other words, each team would make its decisions immediately before executing them.
	
	Under popular demand, this revision to the rules also added new elements as subclasses of the basic ones. Ice and mist stemmed from water; void and light from wind; life and stone from earth; sulfur and darkness from fire. This addition was one alleged reason for the delay in issuing the alteration, although logistic factors likely played a role as well. Nonetheless, this change brought commendation from former detractors, not only for restoring balance between the leaders and the trailers, but also for the extended depth stemming from the gimmicks of each sub-element.
	
	The newfound exposure that the new system received invited an influx of new combatants, and existing ones pushed its limits during the ``second period''. Card combat, at its highest level, required and still requires several years of experience for the average magician. Among those already learned in this style of combat, the second period expansions also fueled the race toward more powerful hits, achieved by stacking amplifiers and lenses, yet nowadays meta-amplifiers, global effects, and infuriations are necessary as well. While most magicians eventually achieve damage values in the millions given controlled settings, only a few enter the esoteric realm of world records (currently \iformone{} points by Anasar Fenma in 1523).
	
	As a result, battle records must be distinguished not only according to period, but also by their purpose -- a legitimate duel or an attempt at a world record impact.
	
	\emph{Card crafting.} The earliest cards were crafted by hand, using a precise tool to carve out gates and tunnels into the material, transforming motes into realizations. However, this process was tedious for all except the simplest cards. Automation of card-crafting began shortly after the first cards; early designs were crude and often gave unexpected results, but machine makers spent their efforts on crafting more precise and reliable devices. Even with the advent of card constructors, however, card-crafting was commonly considered a difficult art.
	
	Although traditionally, sharing card recipes was considered unethical, this act has become better received by most schools and communities in recent years. On the other hand, some figures still oppose it. According to Arsaren Ryson, ``recipe-sharing grants newcomers too much power upfront; it deprives them from understanding the processes by which cards operate'' (1506a). Unsurprisingly, Arsaren holds a strong opinion that students should learn to craft cards by hand before using a machine.
	
	\emph{The dynamics of multi-combatant battles.} While a significant fraction of battles happen between only two magicians, those with more than one combatant per team gain more intrigue. If, as in the common case, the players on a team prefer different elements, then the elemental strengths can interact -- for instance, an earth magician could restore the health of someone who prefers to work with water, or a water magician could transfer amplifiers from opponents to a fire or wind magician. Despite that they are difficult to notate, multi-combatant battles are useful and interesting to study.
	
	\emph{The psychology of Corrupt Sprite.} Available since the beginnings of card-combat, this spell, which reduces the strength of the target's next outgoing attack by one-quarter, has been almost ubiquitously regarded as a --
}

``What the hell are you reading, Vija? At least stay with real science if you like that rubbish.''

Myllada turned her head, noticing Telto standing next to her, hand on the table. ``What's your problem with it? I'm genuinely interested in this topic.''

``Well, Cjanden finished preparing the food.''

Stretching backwards and removing the chair under her, Myllada stood up and followed her friend to the dining room.

\centeredstars

``Thank you for your time.''

Cjanden swung one of her arms back and forth. ``That's fine; I don't want you hungry. I'll be staying around here in case you need me.''

Telto now turned to Myllada. ``I wish all those magicians stuck to the former way of fighting.''

``Are you saying that you want to risk your life in every battle?''

``We're risking our lives anyway. Frankly, it doesn't matter if this is the normal way of fighting with magic, since a whole group of people are breaking all the rules. That is to say, you're squandering your efforts on a skill that you won't be using once we're out of the castle.''

Cjanden interrupted, ``Beware: while the Order of the Serpent might hold immense amounts of power, it is far from invulnerable. There are only so many members, and, finding who meets the criteria for membership, let alone initiating them, takes much effort. Most of their power comes from a secret artifact as well, and when that's destroyed, they are more vulnerable. I warn you: any day, it might again become relevant.''

``I wish,'' Myllada and Telto chanted at the same time and glanced at each other.

``I have something for you two!'' \yronsyncra{} came running into the room, waving a folded sheet of paper.

Telto snatched the piece of paper, opened it, and skimmed its contents before hurriedly handing it to Myllada while muttering ``fuck this''.

Myllada caught the note in her hands.

\q{
	I am pleased to announce that we have finalized a permanent solution to the issue regarding turn order. Effective immediately, all players will decide their moves before any cards are executed, as done before the interim reform, but the turn order will be randomized.
	
	The probability of moving first on a given turn depends on the team's combined initiative score, plus the team that went first on the previous turns. Certain spells shall manipulate initiative score as well.
	
	-- E. R.
}

``Surprised it took thirty-two years to finally issue that change.''

``Look, I don't give a damn about this subject.'' Telto stomped out of the room, through a high arch.

After a moment of silence, the cat began, ``She'll return when she's hungry again.''

Myllada inquired, ``May I pet you, by the way?''

``No.'' Before \yronsyncra{} responded, however, Myllada was already running her gentle hands through her hair. She hissed, making Myllada jump.

Myllada ran a short distance before she slipped and fell flat on her face.

\yronsyncra{} crouched down to her and patted her head. ``Now I must return outside.''

Without a word, Myllada recovered and exited the room through the library entrance.

\centeredstars

The summer sun shone through the glass roof, reminding Myllada of the past days of unbridled ventures and perils while she slogged through tables of past duels, filled with figures, symbols, and arrows. \emph{How am I supposed to make sense of this mess?} She drew a few sheets of paper and held a pencil over one of them. Humming a slow tune, she began by scribbling: making loops, angles, and zig-zags, while peering over the names of cards, some of which she did not recognize. Searching for a list of cards and their effects, she flipped toward the back, to no avail.

Next to the book was the note, which she had reread several times. \emph{This book isn't of much use anymore, and never was anyway. Some of the battles have tables that are too wide for a single page, and they still look cramped.} The scribbles grouped themselves together, forming rough but coherent sketches -- of forests, seas, and mountains.

\centeredstars

Telto heard the creak of the door. ``Vija, why the hell are you visiting for the first time since we came back?''

``I'm not too interested in that book anymore.''

``The red one?''

``Actually, I was talking about another. But I've finished the red book.''

``Do I \emph{look} like someone who wants to read that piece of garbage?''

``From your insult towards that subject, you don't seem so.''

``Well, I've been sitting in my room all day, and I'm full of energy. If you follow me across the castle, then I'll consider it.''

Myllada nodded.

\centeredstars

Telto strolled through the hallways and down a long flight of stairs. ``I've visited here before. No one seems to use any of the rooms.'' She faced one of the doors and turned the knob, revealing a dark, dusty room with a wooden-plank floor. ``I prefer this place -- it's not terribly hot unlike most of them, including mine, during the summer. The downside is that it's always dark, and there are no lights.'' On each step, she kicked some of the dust, exciting it into the air before it stabilized back on the floor.

Myllada touched Telto's shoulder as she blindly stepped around the room, waiting for her eyes to adapt to the darkness.

Telto removed her shoes as she slipped into the bed.

``Isn't it a bit... dusty?''

``Sure.'' Telto shook off the dust from the blanket and ran her hands on top of the mattress, before replacing the blanket. ``There's room for another person.''

Myllada, already walking without anything on her feet, crawled onto the surface.

``I'd like to feel your hair.'' Telto pointed at Myllada's head, where the lavender threads had grown past her shoulders again.

``Go ahead.''

Telto wrapped her arms around Myllada's neck and twisted her fingers into her hair.

Crossing her legs, Myllada advanced her hands toward Telto's sides, stroking them downwards. ``Nice to actually talk to each other in that long of a time. Apologies for getting a bit infatuated and not looking at you.''

``I'm glad the separation wasn't forever.''

Myllada crept out of bed, letting go of Telto, who followed her out of the room. Leading the pair, she sprinted across the hallway with light feet, her hair flying in the air.

``You seem to be able to run a lot faster and longer.''

``I always wonder why.'' Myllada sensed the smell of death, growing stronger as she progressed.

``Vija, one of the doors are bloody!''

As soon as Telto pointed at that door, Myllada swung it open, imparting dead bodies piled around the perimeter of the room, their eyes missing and a trail of blood around them; at the center was a pile of thick blankets, where an emaciated, eyeless person gasped as another hugged the first, with both of them having their SR clothing lifted above their waists and lying deep inside the makeshift bed, next to which rested a box containing a series of wooden-handled knives, stained with blood, and Myllada jumped back with a long shriek.

\chapter{Fear of Losing Sight}

As Myllada bolted in the opposite direction, toward the stairs up, she whispered, ``I fucked up, I fucked up, I fucked up, I fucked up...''

And as Telto followed her, cloak flying around, she heard a slam and looked back. No one behind them.

Myllada kept panting, repeating her confession of her grotesque error. \emph{That might have been why no one used it.} She took two steps at a time up the stairs, trying to handle the pain from her bare feet.

At the top of the stairs, she sat at the uppermost step, looking back at the dark hallway. With an exasperated breath, she moaned, ``What the fuck was that?''

``I counted how many times you said that word.''

``Thanks. What is it?''

``One hundred and one times.''

``But I still don't know what that was. I think they were having --''

``Whoa, don't say that word.''

``I think one of them wanted to lay an egg.''

``Who knows. And how does one of them not have eyes? If that's the case, I'm scared shit of going back down there.'' Telto wiped off drops of sweat off her forehead with her narrow sleeve. ``You almost outran me back there.''

Myllada laughed through her nose. ``Hey, want to race across that hallway?''

``I'm still scared. Let's go.''

\centeredstars

The festival had ended, and those who attended it returned. Myllada and Telto arrived, out of breath and drenched in sweat, into Dernar's room.

``It's been long since we've last seen each other,'' Dernar greeted in a steady voice.

Myllada gasped for air. ``One of the hallways, we need to close it. There's a madman over there.''

``Ah, really. Cjanden would have known about it.''

``So you're the master of the castle and you still don't know about all of the places.''

``I didn't build all of the final structure. Did Telto lead you there?''

``Part of the way. I opened the door, though.''

``Yep,'' declared Telto, ``that was her fault.''

``Well, as much as I'd love to blame Telto, I'll have to blame myself, and myself alone.''

``Very well. Now go bother Cjanden about it.''

\centeredstars

Cjanden directed the two to the same dark room where they previously lay down, and sat on the floor across them. ``Are you really curious?'' she asked in a wicked cackle.

``Yes.''

``Are you really sure?''

``Yes.''

``Are you really stupid?''

``Yes.'' Myllada burst into laughter and almost collapsed backwards onto the floor.

``Are you really tranced?''

``For fuck's sake, I just want to hear the story!'' exclaimed Telto.

``I'll continue, then. In that room is a monster, who, once in a while, exits that room and looks for someone to take in. Takes that person in, and has an array of knives to slice that person's eyes out.''

``Then what, next?''

``She \emph{shanks} `em. Shanks `em until they die. Sometimes even keeps doing it for days before realizing they're dead. Then looks for another person. Luckily she stays in that room otherwise.''

``We need to get out of this hallway. Seal it off, if possible.''

``Few things can stop her, though. Will break through any barrier she can, and she isn't weak either.''

``Let's get out anyway. Never know when she'll come looking for another victim.''

\centeredstars

Telto diverged from Myllada and Cjanden, into her usual room, lazing around as usual. The other two proceeded to the library, now busy as usual (which had relatively few visitors anyway).

Spotting \yronsyncra{} in the distance, Myllada ran up the stairs toward the door.

``How are you doing, Vija?''

``Got a little bored, so I had the experience of my life.'' Myllada's hair was strewn across her face, tangled like the branches of a tree. ``My friend led me into a dark hallway, and we lay down in a bed for some time. I decided to walk farther along, where we saw a door stained with blood. I opened it without thinking, and in the middle of the room... there was someone who had taken the eyes of another before lying in the bed with that person. How was your day outside?''

``Missed some of it to hand you that note, but nearly everyone in the bounds made it there. Ate lots of food, played games, and spoke to many people, particularly magicians from other schools. I pity you and your friend for not being able to attend.''

``By the way, did you see any members of the Order?''

``What order?''

Myllada hesitated and lowered her volume. ``The Order of the Serpent.''

``Actually, I did, but they were all far out, around the outskirts of the Armadereyn. Did you read any books while we were gone? From the library?''

``I tried going through one, records of card battles. Do you want to see it?''

``Sorry, I'm worn down right now. Reach me again in a few hours, and I'll have more energy.''

\centeredstars

After Myllada fruitlessly attempted to comprehend the records, she glanced at the clock and left the book open while she sprinted to the door to the sandstone room and opened it. There were already a few students, most of them above her age, who labored behind their tables, scattered with contraptions and reagents.

Not seeing the cat inside, she gently closed it and crept across the center aisle. \emph{Is she still too tired? Or maybe she's busy.}

From the left, a student, about nineteen years old, behind an infusion apparatus surrounded by flasks of liquid, tapped her hand.

Myllada turned left. ``Yes?''

``Not too common to see someone as young as you here on breaks. It's mostly the advanced students who arrive here at those times.''

``I guess. What are you doing here?''

``Infusion. That is, brewing concoctions. What is your name?''

``Please call me Vija.''

``Is that a nickname?''

``It is.''

``What is your actual name, then?''

Myllada's body went warm before she blurted, ``Cytaen Myllada''.

``Well, you must be shy about it. Mensse Vyror, glad we met. What are you focusing on right now?''

``Card-crafting.''

``You're a fan of cards, aren't you?''

``Obviously.''

``Why are you here?''

``I'm here to check on \yronsyncra.''

``You realize that you're not the only student in this whole building, right? And she's sleeping, too. Just stop pretending she's your best friend, won't you?''

Myllada twisted her mouth. ``Sure thing. It was nice seeing you.'' Promptly, while Vyror distracted himself with infusion, Myllada proceeded down the center.

All of the braziers at the end of the room were unlit. Myllada peeked behind the cat's desk. Inside, next to the chair, \yronsyncra{} had laid down a thick blanket on the floor to sleep, rolling herself into a ball. Myllada pulled back the chair and lay down next to the cat, who purred in her slumber.

\centeredstars

\yronsyncra{} opened her eyes and rolled her body a half turn when she felt a heavy lump behind her. The cat screeched a meow of surprise, causing Myllada to back away on her legs. Making another half turn, \yronsyncra{} rose to her knees and stared at Myllada. ``Vija, what were you doing next to me?'' As other students, who toiled behind their desks, crowded around the front, over her loose, light dress did she pull up her usual garb. ``I'm a sleepy cat, and I want to know why you disturbed me.''

``I was waiting for you to wake up.''

\yronsyncra{} clenched her fist and shot it toward Myllada's stomach, causing her to collapse. ``Bring me a glass of water.''

\centeredstars

By the time \yronsyncra{} had stopped asking for water, Myllada had handed her six from the dining room.

``That's enough for now. Now sit at the front row. I will leave in a half \emph{enean}, at which time I will close this room.''

Some time later, after most of the students had finished their assignments and exited the room, \yronsyncra{} lifted Myllada and mounted her on her back.

\centeredstars

When \yronsyncra{} arrived at her room, she let Myllada slide down the floor and punched her stomach. As she threw off her surface clothing and unbuttoned the top of her sleeping clothes to reveal her shoulders, she com/demanded, ``Remove all of your clothes and kneel next to the bed. Hold up your arms as high as you can.''

Shaken by \yronsyncra's intimidating voice, Myllada threw them all over herself and knelt on the carpeted floor, to the side opposite where the cat lay in bed, under the sheets, while feeling the heat from her body.

The cat began: ``Cytaen Myllada, you are fourteen years old now, and you should have stopped this ass-kissing by now, at least. I was not even fully dressed when I was asleep. Why did you decide to lie down next to me?''

``I was waiting for you to wake up so I could show you what I was reading when you had more energy.''

``I am not your friend, and I do not have the time to focus on one specific student. I have one task inside the room: to teach. Anything else is an unnecessary luxury.''

\emph{Perhaps she's right. But why has she been generous before but changed her heart today?} ``I understand, Instructor.'' As Myllada trembled in fear and regret, blood drained from her arms.

``There is no use in narcissism. Your circumstances do not make you special. You will be treated as anyone else of your level.''

Myllada gave no answer, but continued to sing a noise of misery.

``There is no need to lower your arms. In return for your `favor', what shall you get back?''

``I won't come to class tomorrow.''

``You are not welcome in class until the solstice, and you will not come to class, nor will you enter the library, until then. Do you understand?''

``Yes, Instructor.'' Myllada felt the tears raining down on her face.

``Please stay for a few more hours; no need to lower your arms.''

\chapter{Yet Another Awkward Departure}

Myllada, knowing that she had no right to be there, crept around the perimeters of the library. From a glance at the door to the classroom, it seemed that no one was entering or leaving. She gave a gentle tug at the handle, but the door would not budge. Hoping that no one who cared noticed her, she slid back down the stairs and receded behind the shelves.

Vyror appeared in her path. ``There are no classes today.''

``I figured. What for?''

``Can't find a reason. I'd say that the cat's sick.''

``It's nice to see you again. I have to leave now, sorry.''

``Hope we can meet again when there is.''

Before Vyror finished his farewell, Myllada had already exited the library through the nearest gate.

\centeredstars

\yronsyncra{} was standing straight in front of Dernar. ``I demand an inspection of every single being in this facility.''

Dernar nodded and uttered only one word: ``why?''

\yronsyncra's voice deepened. ``Who do you think you are?'' The cat's ears started drooping and dripping into liquid, followed by her head, and the melted parts vaporized into thin air, revealing another figure. ``And who do you think \emph{I} am? I want all of you to line up and disrobe completely for inspection.''

Dernar, still calm, adjusted her glasses. ``I can't fulfill that request.''

``A foolish administrator. Even if you kill me by some fluke, there are hundreds of others surrounding this place. You -- every student and instructor, every master and servant -- are at our mercy. Do not risk your lives by not heeding our instructions.''

``I now know who you are. You are a member of the order, here to find a certain -- ''

With both of his long-nailed hands, the figure clenched Dernar's neck. ``Say no more or I will push my thumbs. If you say `I agree', then once we depart, all will continue as normal. If you say anything else, then none of you will remain alive, and this castle will be nothing but ruins, expansive fields of crumbling stone brick.''

``I agree.''

The figure released Dernar, dropping her onto the floor as if she were a rag doll.

``All of you are to line up and strip your clothing until the end of the inspection. Hide any people and there will be no survivors.''

\centeredstars

\emph{Surely I'd be allowed to enter the library just to get to the dining room?} Myllada hugged the wall as she concealed herself.

``Vija!''

Myllada turned her head and spotted Dernar behind a bookshelf. She pushed herself off the wall as she started walking. ``Please forgive me. I was going to the dining room.''

``Follow me.'' Dernar held Myllada's hand and dragged her along the edge of the library and into the dining room. ``The Order; they're here to look for you. You need to leave right now.''

``Isn't hiding an option?''

``If they find us, then none of us will live.''

``But my friend, too. And my bag.''

``There isn't enough time for that right now. I'll send Telto up tomorrow. Where shall I tell her to meet you?''

``Tell her to travel through the road west of the village, but take the right fork.''

``It's too dangerous. Anyone could easily track you through that path. Stay at the village instead.''

``Then the Sarynde Bookstore, tomorrow morning.''

``That's a better location. Don't go to places where you'll be spotted, and don't show yourself.'' Dernar handed a folded sheet to Myllada, who was already walking through the exit tunnel.

\centeredstars

Telto walked across the dark hallway with her lantern. Most of the doors were open, but strangely, one of them was completely shut. Without any forethought, she turned the handle and opened it halfway. ``\yronsyncra! Why are you here? What has happened?''

Blood strewn across her face, and emptiness where her eyes used to be, \yronsyncra{} lay down on the floor among a pool of waste. ``Alas, my eyes! I can see no more!''

Backing out of the room, Telto closed the door. ``I'll be back later.''

\centeredstars

``I hope this isn't a prank.'' Dernar followed Telto down the stairs into darkness.

``Rest assured; this is really \yronsyncra.''

``If that's the case, I'll have to thank you for finding her.''

``Well, there's one problem...'' Telto held the knob, but waited a second before turning it and opening the door.

Dernar bent toward \yronsyncra. As she glanced at her face, she raised her own hand over her mouth. ``This is terrible... who would teach in her place? Telto, Myllada has left; you must leave too. Take the exit to the village; she will be waiting for you at the Sarynde bookstore tomorrow morning.''

``But who did this to \yronsyncra?''

``As much as I'd like to say even those of the Order wouldn't be audacious enough to deprive another of her vision, I'll have to suspect their involvement. After all, someone took her place, disguising himself with a potion. I apologize for subjecting us all to that strip search, but the Order will think only once before unleashing a proscribed spell or employing a forbidden device.''

\centeredstars

Having tied the sheet around her head, Myllada stood behind one of the shelves, looking at the door.

``Are you here to buy a book?''

``Sorry, but I'm here to meet someone. Should I find another place?''

``Well, still nice to have you here. Maybe you'd attract more people inside.''

Myllada observed the spines of the books spanning the shelves when the door swung and Telto walked inside.

``Nice to see you again,'' whispered Telto. ``If you thought kneeling naked in front of the angry `instructor' was awkward, we had to stand in a row and take off all our clothes while we could see each other all.''

``That must have been awkward. Is it safe to return yet?'' Myllada adjusted the sheet over her head to reveal a sliver of hair.

``I'm pretty sure we're never completely safe, in any place, but Dernar told us not to return for now.''

``Ah, I see. Where do I change my clothes?''

``What about that back room?''

Myllada pulled on the handle, but the door did not open. ``It's locked. Anyway, where shall we travel from here?''

``It's pretty unlikely they'll look south. Why don't we walk over there?''

``Right now?''

``Sure, a lot of people use that path, so we can get by without being detected.'' Telto handed the bag to Myllada.

\centeredstars

Myllada, her face covered by a mask and her hair cut back short, rested on the stairs of the boundary and looked across the long brick road among a grassy expanse, extending beyond sight. Under all of the clothing she was wearing, she felt like a brick being baked in the desert to which the path allegedly led.

As Myllada rose back up, Telto, her face uncovered, trailed her, eight \emph{eneo} behind as planned, separated by several strangers.

\chapter{Twenty-first chapter}

The sun sank into the western skies, leaving a crimson aura that Myllada had not observed in a long time. Having walked since midday, she turned right and sat down on the porch of a small, old-fashioned inn, legs unfolded, careful not to reveal them or flip her hood.

As Telto approached the porch, she opened the front door, and Myllada followed her inside. In the front room, travelers gathered around tables, reading or talking, and there was a long queue behind the desk.

While waiting in line, Myllada, feeling slightly cooler than outside, clasped her hands in front of and behind her body and waved her arms back and forth. At last, she saw the desk, where a person with hair tied greeted Telto.

``Good evening.''

``Two people, one night.''

``One room, I guess? That's twenty \emph{mearo}.''

Telto laid a few silver coins on the counter.

The clerk inspected the coins for a second and opened a drawer behind; pulled out a key and handed it over. ``Thank you. Your room is on the third floor.''

\centeredstars

As Telto turned the bolt at the door, Myllada removed her outer coat and the sheet over her head, and unmasked herself. She fell face first on the bed, letting the sheets absorb her sweat while she gasped for fresh air.

Leaving the window ajar, Telto pulled the curtains inwards and kicked her shoes off her feet before laying down next to Myllada. ``Finally, we can speak.''

``Could you get me some cold water? My throat is dry, and I don't think I'll live for long if it stays so.''

``Sure,'' replied Telto, slipping her shoes back on and unbolting the door. ``Lock it while I'm away.''

Not long later, Telto returned holding a ceramic jug and two cups, which she unloaded inside before locking the door again. ``They give us water for free.'' She tilted the jar into one of the cups and handed one full of water to Myllada.

The thirsty child, still sitting on the bed, downed the whole glass and returned it to Telto, who, still sipping her own, mindlessly grabbed it from her hands. Feeling sleep drag her down, Myllada collapsed into the soft bed.

\appendix
\showappendices

\achapter{Pronunciation Guide}

The names of people and of many places are in a language named \emph{Necarasso Cryssesa}, meaning ``forest language''. This guide has been provided to help readers pronounce such names correctly. For more details, please consult \emph{A complete grammar of Necarasso Cryssesa}.

\begin{itemize}
	\item \emph{C} is pronounced as in \emph{cat}, never as in \emph{cell}.
	\item \emph{\v{C}} is pronounced as the \emph{ch} in \emph{cheat}.
	\item \emph{G} is pronounced as in \emph{gate}, never as in \emph{gentle}.
	\item \emph{H} is pronounced as in German \emph{Buch}, or \emph{loch} as pronounced in Scottish English. This sound is to \emph{k} as \emph{th} is to \emph{t}.
	\item \emph{J} is pronounced as the \emph{y} in \emph{yell}.
	\item \emph{L} is always pronounced in a light fashion, as in \emph{let}, as opposed to \emph{well}.
	\item \emph{Ll} is to \emph{s} as \emph{l} is to \emph{r}.
	\item \emph{R} is pronounced as in English, except when it follows another \emph{r} before a vowel, in which case it is pronounced like the \emph{w} in \emph{window}, except with the lips unrounded.
	\item \emph{S} is an \emph{s} sound, except when it is adjacent to a voiced sound, in which case it is pronounced as a \emph{z}.
	\item \emph{Ss}, similarly, is the \emph{th} in \emph{thin}, except when it is adjacent to a voiced sound, in which case it is the \emph{th} in \emph{there}.
	\item \emph{\v{S}} is pronounced as the \emph{sh} in \emph{shell}.
	\item \emph{Css} is a simultaneous pronunciation of the Necarasso Cryssesa \emph{h} and \emph{ss}.
	\item Technically speaking, \emph{f} and \emph{v} are pronounced with the lips touching each other, but this difference rarely matters.
	\item The sounds represented by \emph{c}, \emph{f}, \emph{h}, \emph{ll}, \emph{p}, \emph{s}, \emph{ss}, and \emph{t} are pronounced like the \emph{t} in \emph{top} as opposed to the \emph{t} in \emph{stop}, even though English does not pronounce all of the sounds listed as the former.
	\item \emph{A} is near the \emph{o} in \emph{cot}, although it is pronounced with the tongue closer to the front.
	\item \emph{E} is pronounced as the \emph{e} in \emph{pen}.
	\item \emph{I} and \emph{y} are pronounced as the \emph{ee} in \emph{feed}.
	\item \emph{O} is the initial state of the \emph{o} in \emph{code}; i.~e.~it does not have any glide.
	\item \emph{I} is always long, and \emph{y} is always short. Other vowels are long if and only if they end a word, or they precede a vowel, \emph{r}, or \emph{ll}. \emph{E} and \emph{o} are pronounced with a more open mouth when they are long.
\end{itemize}

\achapter{Other remarks}

As customary in \emph{Necarasso Cryssesa}, full names are given with the surname first, followed by the given name. For example, \emph{Cytaen Myllada} would be referred at most times by her given name \emph{Myllada}; academic works would generally refer to her by her surname \emph{Cytaen}.

Surnames are passed from parent to child in an unusual method.

\centeredstars

As the setting and plot are located on a different planet than the one on which you reside, this book uses \emph{Necarasso Cryssesa} units. It is too tedious to list all of them here; as a result, please consult the \emph{Complete grammar of Necarasso Cryssesa}.

Time is not always expressed in \emph{Necarasso Cryssesa} units, but rather only when it measures a specific interval of time.